---
---

```{r include = F, eval = F}
info <- items(start = td("2023-09-13"), end = td("2025-02-28"), finish = td(NA),
  id = "BSZD230913", client = "朱彤", inst = "",
  type = "生信分析",
  title = "相分离",
  save = ".items_analysis.rds"
)
show.ic(info)

order_publish.bosai("analysis.Rmd", "analysis_out.Rmd")
idname <- formatName.bosai("./analysis_out.docx")
order_packaging("./analysis_out.docx", idname = idname, external_file = NULL)
```

```{r include = F}
#| setup
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
autor_preset()
## the package are available at <https://github.com/shaman-yellow/utils.tool>
## if you want to run codes of this Rmarkdown,
## please install the package `utils.tool` and other related packages (run
## install.R)
options(savedir = list(figs = "Figure+Table", tabs = "Figure+Table"))
```

```{r eval = T, echo = F, results = "asis"}
set_cover.bosai(info)
```

```{r eval = T, echo = F, results = "asis"}
set_index()
```

# 分析流程 {#abstract}

```{r}
dic(di("差异表达基因"),
  di("相分离")
)

```

```{r}
#| route
route <- as_network(
  list("Phase_separation:DB_PhaSepDB",
    ":, ",
    ), "sugiyama"
)
p.route <- flowChart(route, 1.1, 1)
p.route
```

```{r eval = T, echo = F, results = "asis"}
#| Route
autor(p.route)
```


# 材料和方法 {#introduction}

```{r eval = T, echo = F, results = "asis"}
collate_details("meth")
```

# 分析结果 {#workflow}

## PhaSepDB 相分离相关蛋白 (LLPS)

`r snap(ps.llps, 0:1)`

```{r}
ps.llps <- job_ps()
ps.llps <- step1(ps.llps)
#' @meth {get_meth(ps.llps)}
ps.llps@params$p.location
ps.llps@params$p.org
feature(ps.llps)
```

## GEO 数据差异分析 (Primary vs Normal)

### GSE 数据搜索 (OS_NORMAL)

`r snap(gds.os_normal, 0:3)`

```{r}
gds.os_normal <- job_gds(c("Osteosarcoma"))
#' @meth {get_meth(gds.os_normal)}
gds.os_normal <- step1(gds.os_normal, expects = m)

vis(gds.os_normal)
active(gds.os_normal)

```

### GEO 数据获取 (NORMAL_GSE234998)

`r snap(geo.normal_GSE234998, 0:2)`

```{r}
geo.normal_GSE234998 <- job_geo("normal_GSE234998")
geo.normal_GSE234998 <- step1(geo.normal_GSE234998)
metadata.normal_GSE234998 <- expect(geo.normal_GSE234998, geo_cols())
metadata.normal_GSE234998
#' @meth {get_meth(geo.normal_GSE234998)}
geo.normal_GSE234998 <- step2(geo.normal_GSE234998)
```


### Limma 差异分析 (NORMAL_GSE234998)

`r snap(lm.normal_GSE234998, 0:3)`

```{r}
lm.normal_GSE234998 <- asjob_limma(geo.normal_GSE234998, metadata.normal_GSE234998)
lm.normal_GSE234998 <- filter(
  lm.normal_GSE234998, type = "metadata", grpl(group, "localized|local_control")
)
lm.normal_GSE234998 <- step1(lm.normal_GSE234998)
#' @meth {get_meth(lm.normal_GSE234998)}
lm.normal_GSE234998 <- step2(
  lm.normal_GSE234998, localized - local_control,
  use = "P", cut.fc = .5
)
lm.normal_GSE234998 <- step3(lm.normal_GSE234998)
```

### GEO 数据获取 (NORMAL_GSE218035)

`r snap(geo.normal_GSE218035, 0:2)`

```{r}
geo.normal_GSE218035 <- job_geo("normal_GSE218035")
#' @meth {get_meth(geo.normal_GSE218035)}
geo.normal_GSE218035 <- step1(geo.normal_GSE218035)
metadata.normal_GSE218035 <- expect(geo.normal_GSE218035, geo_cols(sample = "title"))
metadata.normal_GSE218035$group
geo.normal_GSE218035 <- step2(geo.normal_GSE218035, rna = FALSE)
data_GSE218035 <- read_genes_from_files(geo.normal_GSE218035@params$dir_files)
```

### Limma 差异分析 (NORMAL_GSE218035)

`r snap(lm.normal_GSE218035, 0:3)`

```{r}
lm.normal_GSE218035 <- job_limma_normed(
  data_GSE218035$data, metadata.normal_GSE218035, data_GSE218035$annotation
)
#' @meth {get_meth(lm.normal_GSE218035)}
lm.normal_GSE218035 <- step1(lm.normal_GSE218035)
lm.normal_GSE218035 <- step2(
  lm.normal_GSE218035, Osteosarcoma_sample - Normal_adjacent_tissue,
  use = "P", cut.fc = .5
)
lm.normal_GSE218035@tables$step2$tops$`Osteosarcoma_sample - Normal_adjacent_tissue`
```

### GEO 数据获取 (NORMAL_GSE99671)

`r snap(geo.normal_GSE99671, 0:2)`

```{r}
geo.normal_GSE99671 <- job_geo("normal_GSE99671")
#' @meth {get_meth(geo.normal_GSE99671)}
geo.normal_GSE99671 <- step1(geo.normal_GSE99671)
metadata.normal_GSE99671 <- expect(
  geo.normal_GSE99671, geo_cols(sample = "title", group = "tumor")
)
metadata.normal_GSE99671
metadata.normal_GSE99671 <- dplyr::mutate(
  metadata.normal_GSE99671, sample = s(sample, "[A-Z]_[^_]+$", ""),
  sample = paste0(sample, substr(group, 1, 1))
)
metadata.normal_GSE99671

geo.normal_GSE99671 <- step2(
  geo.normal_GSE99671, "filecounts", rna = FALSE
)
counts.GSE99671 <- ftibble(geo.normal_GSE99671$dir_files)
genes.GSE99671 <- dplyr::select(counts.GSE99671, 1:3)
counts.GSE99671 <- dplyr::select(counts.GSE99671, 1, dplyr::where(is.integer))

metadata.normal_GSE99671 <- dplyr::filter(metadata.normal_GSE99671, sample %in% colnames(counts.GSE99671))
metadata.normal_GSE99671
```

### Limma 差异分析 (NORMAL_GSE99671)

`r snap(lm.normal_GSE99671, 0:3)`

```{r}
lm.normal_GSE99671 <- job_limma(
  new_dge(metadata.normal_GSE99671, counts.GSE99671, genes.GSE99671)
)
lm.normal_GSE99671 <- step1(lm.normal_GSE99671)
#' @meth {get_meth(lm.normal_GSE99671)}
lm.normal_GSE99671 <- step2(
  lm.normal_GSE99671, TUMOR - NORMAL,
  use = "P", cut.fc = .5
)
lm.normal_GSE99671@tables$step2$tops$`TUMOR - NORMAL`
```


## TCGA 数据获取 (OS)

`r snap(tcga.os, 0:3)`

```{r}
#' @meth {get_meth(tcga.os)}
tcga.os <- job_tcga("TARGET-OS")
tcga.os <- step1(tcga.os)
tcga.os <- step2(tcga.os)
tcga.os <- step3(tcga.os)
```

# 总结 {#conclusion}

