---
---

```{r include = F, eval = F}
deparse_mail()
info <- items(belong = odate(3), eval = ic(1, 2, 1, 2, 0), lock = T)
show.ic(info)

order_publish()
idname <- order_packaging()
```

```{r include = F}
#| setup
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
autor_preset()
## the package are available at <https://github.com/shaman-yellow/utils.tool>
## if you want to run codes of this Rmarkdown,
## please install the package `utils.tool` and other related packages (run
## install.R)
options(savedir = list(figs = "Figure+Table", tabs = "Figure+Table"))
```

```{r eval = T, echo = F, results = "asis"}
set_cover(info$title)
```

```{r eval = T, echo = F, results = "asis"}
set_index()
```

# 摘要 {#abstract}

```{r}
dic(di("差异表达基因", "Differential Expressed Genes", "DEGs"),
  di("腰椎间盘突出")
)

# DEGs: Differential Expressed Genes 差异表达基因
# LDH: Lumbar disc herniation 腰椎间盘突出
```

PMID：37392674

The TCMSP system (Ru et al., 2014) was used to retrieve the main chemical
components of the individual herbs Da Huang (DH), Hong Hua (HH), Huang Qi (HQ)
and Dan Shen (DS) (Table 1). Those characterized by OB ≥ 30% and DL ≥ 0.18 and
their corresponding targets were obtained. A search for “Diabetic Kidney
Disease” was performed in five databases (Zhu et al., 2021) of GenGards, OMIM,
drugbank, TTD, and Disgenet, to identify candidate targets. The diabetic
nephropathy targets was mapped with the drug action targets to obtain the
intersection target and a Venny map was drawn. The intersection targets were
imported into the String database for PPI analysis and then the results were
visualized via Cytoscape 3.9.0. GO and KEGG analysis of intersection targets
were performed using the Metascape database (Zhou et al., 2019), and GO
information histograms and bubble maps of pathway information were drawn on
WeLifeInfo.

PMID：36288650

Active compounds of each herb in the SSW formula were obtained by searching the
Traditional Chinese Medicine Systems Pharmacology (TCMSP)
(http://lsp.nwu.edu.cn/tcmsp.php) and Encyclopedia of Traditional Chinese
Medicine (ETCM) (http://www.tcmip.cn/ETCM/index.php/Home/Index/) databases
(Ru et al., 2014; Xu et al., 2019; Zhang et al., 2019). We set the cutoff of
oral bioavailability (OB) ≥ 30% and drug-likeness (DL) ≥ 0.18 in TCMSP and
drug-likeness grading ≥ 0.49 in ETCM as the threshold for the active
substances.

Insomnia-related targets were mined from the Online Mendelian Inheritance in
Man (OMIM; https://omim.org/), DisGeNET (http://www.disgenet.org/), GeneCards
(https://www.genecards.org/), Drugbank (https://go.drugbank.com/), Therapeutic
Target Database (TTD; http://db.idrblab.net/ttd/), PharmGKB
(https://www.pharmgkb.org/) and Malacards (https://www.malacards.org/)
databases, and we selected targets with relevant score > 1 in GeneCards
database. All gene targets were normalized to the STRING database
(https://string-db.org/) to eliminate redundancy.

Network establishment and analysis The TCM compound-target-disease network was
established by calculating the relationship between nodes, representing the
information collected from the databases. The molecular association between
drugs and diseases was determined based on the network to explain the overall
mechanism of action of the TCM compounds through functional analysis
(Luo et al., 2020).

The intersection between the targets of active compounds in SSW and insomnia
genes was visualized using VENNY 2.0.2
(https://bioinfogp.cnb.csic.es/tools/venny/index2.0.2.html). These intersection
targets were used to establish a protein-protein interaction network using
Cytoscape software (Version 3.8.2). Each node represents a target, and the
edges represent whether there is a linkage between the targets and high-quality
interactomes. The degree represents the number of source node-linked target
nodes, which indicates the topological importance of nodes in the network;
nodes with degrees larger than 20 were considered hub targets. Degree analysis
was performed using the network analyzer tool CytoHubba.

PMID：38295661

Identification of the compounds in QHZYF by UPLC-Q-TOF/MS


# 前言 {#introduction}

# 材料和方法 {#methods}

## 材料

```{r eval = T, echo = F, results = "asis"}
auto_material()
```

## 方法

```{r eval = T, echo = F, results = "asis"}
auto_method()
```

# 分析结果 {#results}

# 结论 {#dis}

# 附：分析流程 {#workflow}

```{r}
gm <- job_gmix("Lumbar disc herniation", "herniation")
gm <- step1(gm)
gm <- step2(gm)
```
