---
---

```{r include = F}
#| setup
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
autor_preset()
## the package are available at <https://github.com/shaman-yellow/utils.tool>
## if you want to run codes of this Rmarkdown,
## please install the package `utils.tool` and other related packages (run
## install.R)
options(savedir = list(figs = "Figure+Table", tabs = "Figure+Table"))
```

```{r eval = T, echo = F, results = "asis"}
set_index()
```

# 摘要 {#abstract}

- 药物成分，Tab. \@ref(tab:Components-of-Herbs)
- 药物-成分-靶点，Fig. \@ref(fig:Herbs-compounds-and-targets), Tab. \@ref(tab:tables-of-Herbs-compounds-and-targets)
- IgA 肾炎相关基因，Fig. \@ref(fig:DEGs-of-GSE175759), Tab. \@ref(tab:tables-of-DEGs-of-GSE175759)
- 靶点-IgA肾炎相关基因（交集），Fig. \@ref(fig:intersection-of-IgAN-DEGs-with-herbs-targets)
- 治疗肾炎相关成分，Tab. \@ref(tab:relative-compounds-of-Herbs-that-treating-IgAN)
- PPI 网络，Fig. \@ref(fig:PPI-networks), Fig. \@ref(fig:MCC-top30)
- ...

# 附：分析流程 {#workflow}

## 成分和靶点

### 成分（白茅根和王不留行子）

```{r}
hb <- job_herb(c("白茅根", "王不留行"))
hb@params$herbs_info %<>% slice(1, 5)
hb@params$herbs_info

hb <- step1(hb)
hb <- step2(hb, 100)
hb <- step3(hb, "IgA glomerulonephritis")
```

```{r eval = T, echo = F, results = "asis"}
#| Herbs-information
autor(hb@params$herbs_info)
```

```{r eval = T, echo = F, results = "asis"}
#| Components-of-Herbs
autor(hb@tables$step1$herbs_compounds, key = "Ingredient.name")
```

```{r eval = T, echo = F, results = "asis"}
#| intersection-of-all-compounds
autor(hb@plots$step3$p.herbs_compounds)
```

### 成分靶点

```{r eval = T, echo = F, results = "asis"}
#| tables-of-Herbs-compounds-and-targets
autor(hb@params$easyRead)
```

```{r eval = T, echo = F, results = "asis"}
#| Herbs-compounds-and-targets
autor(p.allu)
```

```{r}
data.allu <- select(hb@params$easyRead, Herb_pinyin_name, Ingredient.name, Target.name)
data.allu <- filter(data.allu, !is.na(Target.name))
p.allu <- new_allu(data.allu, axes = 1:3, label.auto = T, label.freq = 20)
```

## IgA 肾炎 (IgA Nephropathy) 差异基因

### GSE175759: RNA-seq profiling for manulaly microdissected tubulointerstitial tissue from 90 kidney samples.

```{r eval = T, echo = F, results = "asis"}
#| metadata-of-used-samples-of-GSE175759
autor(as_tibble(lm@params$normed_data$targets), key = "group")
```

```{r eval = T, echo = F, results = "asis"}
#| DEGs-of-GSE175759
autor(lm@plots$step2$p.valcano[[1]])
```

```{r eval = T, echo = F, results = "asis"}
#| tables-of-DEGs-of-GSE175759
autor(lm@tables$step2$tops[[1]])
```

```{r}
geo2 <- job_geo("GSE175759")
geo2 <- step1(geo2)
geo2 <- step2(geo2)
untar("./GSE175759/GSE175759_RAW.tar", exdir = "./GSE175759")
lapply(list.files("./GSE175759", "\\.gz$", full.names = T), R.utils::gunzip)
```

```{r}
metadata <- filter(geo2@params$guess, diagnosis.ch1 %in% c("Control", "IgAN"), technical.outlier.ch1 == "No")
metadata <- dplyr::rename(metadata, sample = rownames, group = diagnosis.ch1)

fun <- function() {
  files <- list.files("./GSE175759/", "GSM.*", full.names = T)
  names(files) <- gs(get_realname(files), "(GSM[0-9]+).*", "\\1")
  files <- files[ names(files) %in% metadata$sample ]
  lst <- sapply(files, ftibble, simplify = F)
  lst <- lapply(lst, dplyr::rename, value = 2)
  data <- data.table::rbindlist(lst, idcol = T)
  data <- tidyr::spread(data, .id, value)
  as_tibble(data)
}
counts <- dplyr::mutate(fun(), id = gs(id, "\\.[0-9]*$", ""))

mart <- new_biomart()
genes <- filter_biomart(mart, general_attrs(), "ensembl_gene_id", counts$id)
genes <- dplyr::relocate(genes, ensembl_gene_id, hgnc_symbol)
```

```{r}
lm <- job_limma(new_dge(metadata, counts, genes))
lm <- step1(lm)
lm <- step2(lm, IgAN - Control, use = "adj")
lm@plots$step2$p.valcano[[1]]
```

## PPI 网络药理

```{r eval = T, echo = F, results = "asis"}
#| intersection-of-IgAN-DEGs-with-herbs-targets
autor(p.venn)
```

```{r eval = T, echo = F, results = "asis"}
#| PPI-networks
autor(wrap(sdb@plots$step1$p.ppi, 5, 4))
```

```{r eval = T, echo = F, results = "asis"}
#| MCC-top30
autor(sdb@plots$step1$p.mcc)
```

```{r}
sets.td <- list(targets = hb@params$easyRead$Target.name, DEGs = lm@tables$step2$tops[[1]]$hgnc_symbol)
sets.td <- lapply(sets.td, rm.no)

p.venn <- new_venn(lst = sets.td)
ins.td <- ins(lst = sets.td)
```

```{r}
sdb <- asjob_stringdb(ins.td)
sdb <- step1(sdb)
sdb@plots$step1$p.mcc
```

## 治疗 IgA 肾炎相关成分

```{r eval = T, echo = F, results = "asis"}
#| relative-compounds-of-Herbs-that-treating-IgAN
autor(rel.cpd, key = "Ingredient.name")
```

```{r}
rel.cpd <- filter(hb@params$easyRead, Target.name %in% ins.td)
```
