

检测或预测 RBP 位点
炎症相关疾病
scRNA-seq
RNA velocity: PhyloVelo, cellDancer


- Four Types of RNA Modification Writer-Related lncRNAs Are Effective
  Predictors of Prognosis and Immunotherapy Response in Serous Ovarian
  Carcinoma

- Survey of the binding preferences of RN
  A-binding proteins to RNA editing events

- Affinity regression predicts the recognition code of nucleic acid-binding proteins

```{r}
tkid <- ftibble("./test/GTEx_Analysis_v8_sQTL/Kidney_Cortex.v8.sgenes.txt.gz")
tt <- ftibble("./test/hg19.txt")
```

```{r}
```


```{r eval = T, echo = F, results = "asis"}
#| IgA-Quality-Control
autor(sr.iga@plots$step1$p.qc)
```

```{r eval = T, echo = F, results = "asis"}
#| IgA-UMAP-Clustering
autor(sr.iga@plots$step3$p.umap)
```

```{r eval = T, echo = F, results = "asis"}
#| IgA-SCSA-Cell-type-annotation
autor(sr.iga@plots$step6$p.map_scsa)
```

```{r}
skel(.job_monocle(), "bc", "B_cell$")
mn.bc <- do_monocle(srs, "B_cell$")

mn.bc <- step1(mn.bc)
mn.bc@plots$step1$p.prin
mn.bc <- step2(mn.bc, "Y_5")
mn.bc@plots$step2$p.pseu
mn.bc <- step3(mn.bc)
mn.bc@plots$step3$gene_module_heatdata$graph_test.sig

sr_sub.bc <- asjob_seurat(mn.bc, 5, rename = "B_cell$_bc")
vis(sr_sub.bc, "regroup.hclust")

mn.bc <- clear(mn.bc)

sr.bc <- map(sr.bc, sr_sub.bc, "scsa_cell", "regroup.hclust")
vis(sr.bc, "cell_mapped")
vis(sr.bc, "scsa_cell")

sr.bc <- clear(sr.bc)
NULL

```


```{r}
en <- job_enrich(unique(bm@params$edqtl$ref_gene), bm$anno)
sig(en) <- "Matched genes"
en@object
```

```{r}
gse@step <- 1L
gse <- step2(gse, c("hsa01100"))
gse@plots$step2$p.code
gse <- step3(gse, c("hsa01100"))
```

### Proximal tubular cells

```{r}
gse.pr <- asjob_gsea(srs, "Proximal")
gse.pr <- step1(gse.pr)
gse.pr@plots$step1$p.go
```

## Communication

```{r}
```

# 研究设计流程图 {#route}

```{r}
#| route
route <- as_network(
  list("RNA_seq_data:Preprocess",
    ), "tree"
)
p.route <- flowChart(route, 1.1, 1)
```

```{r, eval = T, echo = F, fig.width = 10, fig.height = 7, fig.cap = NULL}
p.route
```


ADAR1 [@TheRoleOfRnaSong2022]

```{r}


fun <- function() {
  g.list <- gse@tables$step1$table_kegg$geneName_list
  ref <- unique(bm@params$edqtl$ref_gene)
  isThat <- vapply(g.list, FUN.VALUE = logical(1),
    function(lst) {
      any(lst %in% ref)
    })
  data <- filter(gse@tables$step1$table_kegg, isThat)
  list(data = data, id = data$ID)
}
lst.find <- fun()
```


## IgA WES 数据

```{r}
# 19-21
qpdf::pdf_subset("./article_supp_wes/JOIM-281-189-s001.pdf", 19:21, "./article_supp_wes/supp19_21.pdf")
# https://www.totalpdf.com/pdf_ocr_excel
supp.wes <- fxlsx("./article_supp_wes/supp19_21.xlsx", startRow = 2)
supp.wes <- select(supp.wes, -1)
supp.wes <- filter(supp.wes, !is.na(GENE.SYMBOL))
supp.wes <- mutate(supp.wes, variant_id = paste0("chr", CH.R, "_", POS, "_", REF, "_", ALT, "_b38"))

supp.match <- filter(supp.wes, variant_id %in% ed@object$signif_variant_site_pairs$variant_id)

```
