---
---

```{r include = F}
#| setup
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
autor_preset()
## the package are available at <https://github.com/shaman-yellow/utils.tool>
## if you want to run codes of this Rmarkdown,
## please install the package `utils.tool` and other related packages (run
## install.R)
options(savedir = list(figs = "Figure+Table", tabs = "Figure+Table"))
deparse_mail()
```

```{r eval = T, echo = F, results = "asis"}
set_index()
```

# 摘要 {#abstract}

- RNA editing underlies genetic risk of common inflammatory diseases
  [@RnaEditingUndLiQi2022]
  (Here we show that ADAR-mediated adenosine-to-inosine RNA editing, a
  post-transcriptional event vital for suppressing cellular double-stranded RNA
  (dsRNA)-mediated innate immune interferon responses5-11, is an important
  potential mechanism underlying genetic variants associated with common
  inflammatory diseases)

检测或预测 RBP 位点
炎症相关疾病
scRNA-seq
RNA velocity: PhyloVelo, cellDancer

```{r}
je <- job_esearch("RNA editing")
vis(je, "Nature")

je1 <- job_esearch("RBPs prediction")
vis(je1, "Nature")

je2 <- job_esearch("RNA editing scRNA-seq")
vis(je2)
```

# 前言 {#introduction}

# 研究设计流程图 {#route}

```{r}
#| route
route <- as_network(
  list("RNA_seq_data:Preprocess",
    ), "tree"
)
p.route <- flowChart(route, 1.1, 1)
```

```{r, eval = T, echo = F, fig.width = 10, fig.height = 7, fig.cap = NULL}
p.route
```

# 材料和方法 {#methods}

## 材料

```{r eval = T, echo = F, results = "asis"}
auto_material()
```

## 方法

```{r eval = T, echo = F, results = "asis"}
auto_method()
```

# 分析结果 {#results}

# 结论 {#dis}

# 附：分析流程 {#workflow}

```{r}
tkid <- ftibble("./test/GTEx_Analysis_v8_sQTL/Kidney_Cortex.v8.sgenes.txt.gz")
```
