cbind(srn.os@object[[ "RNA"]]$counts.BC2, srn.os@object[[ "RNA"]]$counts.BC3)
CreateSeuratObject(counts = cbind(pbmc.stim, pbmc.ctrl), project = "PBMC", min.cells = 5)
test <- srn.os@object[[ "RNA"]] %>% integrateLayers
test <- Seurat::NormalizeData(test)
test <- Seurat::FindVariableFeatures(test)
test <- Seurat::ScaleData(test)
test <- Seurat::RunPCA(test)
test <- harmony::RunHarmony(test, ".layer")


```{r}
scflocal.os <- asjob_scfea(srn.os, org = "human", dir = "scfea_local")
scflocal.os@step <- 0L
scflocal.os <- step1(scflocal.os)
```


## CopyKAT 癌细胞鉴定 (BC3)

```{r}
sr.bc3 <- job_seurat("./GSE152048/BC3/", "BC3")
kat.bc3 <- asjob_kat(sr.bc3)
kat.bc3 <- step1(kat.bc3)
kat.bc3 <- step2(kat.bc3)
kat.bc3 <- step3(kat.bc3)
kat.bc3@plots$step3$p.copykat
clear(kat.bc3)
# kat.bc3 <- readRDS("./kat.bc3.3.rds")
```

## Seurat 癌细胞注释 (OS)

```{r}
kat.bc2@tables$step2$res_copykat
srn.os <- merge(srn.os, kat.bc2, "ChatGPT_cell")
srn.os <- merge(srn.os, kat.bc3, "copykat_cell")
srn.os <- mutate(srn.os, isCancer = ifelse(copykat_cell == "Cancer cell", "Cancer", "Normal"))
wrap(srn.os$p.map_cancer, 8, 6)
vis(srn.os, "isCancer")

wrap(srn.os@plots$step6$p.map_gpt, 8, 6)
```

sr.cb_ob_pob <- asjob_seurat_sub(
  srn.os, grpl(scsa_cell, "Proliferating_osteoblastic_OS|Osteoblastic_OS|Chondroblastic_OS")
)

sr.bc20@object <- NULL
sr.bc20 <- set_remote(sr.bc20)

set_remoteRun.bosai(1)
test <- run_job_remote(sr.bc20, {
  x@object <- eg
  x@step <- x@step + as.integer(1)
})
test@sig
