

### GEO 数据获取 (PB_GSE89376)

`r snap(geo.pb_GSE89376, 0:2)`

```{r}
geo.pb_GSE89376 <- job_geo("pb_GSE89376")
#' @meth {get_meth(geo.pb_GSE89376)}
geo.pb_GSE89376 <- step1(geo.pb_GSE89376)

metadata.pb_GSE89376 <- expect(geo.pb_GSE89376, geo_cols())
metadata.pb_GSE89376$cell.type.ch1
```

### GEO 数据获取 (GSE210797)

`r snap(geo.pl_GSE210797, 0:2)`

```{r}
geo.pl_GSE210797 <- job_geo("GSE210797")
#' @meth {get_meth(geo.pl_GSE210797)}
geo.pl_GSE210797 <- step1(geo.pl_GSE210797)
geo.pl_GSE210797 <- step2(geo.pl_GSE210797)
metadata.pl_GSE210797 <- expect(geo.pl_GSE210797, geo_cols())
```

test <- sr.sepsis@object %>% Seurat::VariableFeatures()
varFeature <- test[ test %in% feature(venn.bulk) ]
sr.sepsis <- focus(sr.sepsis, varFeature, name = "var")
sr.sepsis@params$focus_var$p.dim

### GEO 数据获取 (PB_GSE232753)

`r snap(geo.pb_GSE232753, 0:2)`

```{r}
rm(geo.pb_GSE232753, lm.pb_GSE232753, metadata.pb_GSE232753)
geo.pb_GSE232753 <- job_geo("pb_GSE232753")
#' @meth {get_meth(geo.pb_GSE232753)}
geo.pb_GSE232753 <- step1(geo.pb_GSE232753)
geo.pb_GSE232753 <- step2(geo.pb_GSE232753)
metadata.pb_GSE232753 <- expect(geo.pb_GSE232753, geo_cols())
metadata.pb_GSE232753
```

### Limma 差异分析 (PB_GSE232753)

`r snap(lm.pb_GSE232753, 0:3)`

```{r}
lm.pb_GSE232753 <- asjob_limma(geo.pb_GSE232753, metadata.pb_GSE232753)
lm.pb_GSE232753 <- step1(lm.pb_GSE232753)
#' @meth {get_meth(lm.pb_GSE232753)}
lm.pb_GSE232753 <- step2(
  lm.pb_GSE232753, sepsis - none
)
lm.pb_GSE232753 <- step3(lm.pb_GSE232753)
lm.pb_GSE232753@plots$step2$p.volcano$`sepsis - none`
lm.pb_GSE232753@tables$step2$tops$`sepsis - none`
```


### GEO 数据获取 (PB_GSE65682)

`r snap(geo.pb_GSE65682, 0:2)`

```{r}
rm(geo.pb_GSE65682)
geo.pb_GSE65682 <- job_geo("pb_GSE65682")
#' @meth {get_meth(geo.pb_GSE65682)}
geo.pb_GSE65682 <- step1(geo.pb_GSE65682)

metadata.pb_GSE65682 <- expect(geo.pb_GSE65682, geo_cols())
metadata.pb_GSE65682$icu_acquired_infection_paired.ch1
```



### GEO 数据获取 (PB_GSE168442)

`r snap(geo.pb_GSE168442, 0:2)`

```{r}
geo.pb_GSE168442 <- job_geo("pb_GSE168442")
#' @meth {get_meth(geo.pb_GSE168442)}
geo.pb_GSE168442 <- step1(geo.pb_GSE168442)

metadata.pb_GSE168442 <- expect(geo.pb_GSE168442, geo_cols())
```

### GEO 数据获取 (PB_GSE168442)

`r snap(geo.pb_GSE168442, 0:2)`

```{r}
geo.pb_GSE168442 <- job_geo("pb_GSE168442")
rm(geo.pb_GSE168442)
#' @meth {get_meth(geo.pb_GSE168442)}
geo.pb_GSE168442 <- step1(geo.pb_GSE168442)

metadata.pb_GSE168442 <- expect(geo.pb_GSE168442, geo_cols())
```

### GEO 数据获取 (PB_GSE137340)

`r snap(geo.pb_GSE137340, 0:2)`

```{r}
geo.pb_GSE137340 <- job_geo("pb_GSE137340")
rm(geo.pb_GSE137340, lm.pb_GSE137340)
#' @meth {get_meth(geo.pb_GSE137340)}
geo.pb_GSE137340 <- step1(geo.pb_GSE137340)

metadata.pb_GSE137340 <- expect(geo.pb_GSE137340, geo_cols(group = "diagnosis"))
metadata.pb_GSE137340 <- dplyr::mutate(
  metadata.pb_GSE137340, group = ifelse(
    grpl(group, "Sepsis|Septic"), "Sepsis", group
  )
)
metadata.pb_GSE137340
```

### Limma 差异分析 (PB_GSE137340)

`r snap(lm.pb_GSE137340, 0:3)`

```{r}
lm.pb_GSE137340 <- asjob_limma(geo.pb_GSE137340, metadata.pb_GSE137340)
lm.pb_GSE137340 <- filter(
  lm.pb_GSE137340, type = "metadata", grpl(group, "Healthy|Sepsis")
)
lm.pb_GSE137340 <- step1(lm.pb_GSE137340)
#' @meth {get_meth(lm.pb_GSE137340)}
lm.pb_GSE137340 <- step2(
  lm.pb_GSE137340, Sepsis - Healthy
)
lm.pb_GSE137340 <- step3(lm.pb_GSE137340)
lm.pb_GSE137340@plots$step2$p.volcano$`Sepsis - Healthy`
lm.pb_GSE137340@tables$step2$tops$`Sepsis - Healthy`
```

### GEO 数据获取 (PB_GSE72326)

`r snap(geo.pb_GSE72326, 0:2)`

```{r}
geo.pb_GSE72326 <- job_geo("pb_GSE72326")
#' @meth {get_meth(geo.pb_GSE72326)}
geo.pb_GSE72326 <- step1(geo.pb_GSE72326)
rm(geo.pb_GSE72326, lm.pb_GSE72326)

metadata.pb_GSE72326 <- expect(geo.pb_GSE72326, geo_cols(group = "group"))
metadata.pb_GSE72326 <- dplyr::mutate(
  metadata.pb_GSE72326, group = ifelse(
    group == "Healthy_control_of_sepsis_and_kidney_disease", "Healthy_control_of_sepsis", group
  )
)
metadata.pb_GSE72326
```

### Limma 差异分析 (PB_GSE72326)

`r snap(lm.pb_GSE72326, 0:3)`

```{r}
lm.pb_GSE72326 <- asjob_limma(geo.pb_GSE72326, metadata.pb_GSE72326)
lm.pb_GSE72326 <- filter(
  lm.pb_GSE72326, type = "metadata", grpl(group, "Healthy_control_of_sepsis|ICU_sepsis")
)
lm.pb_GSE72326 <- step1(lm.pb_GSE72326)
#' @meth {get_meth(lm.pb_GSE72326)}
lm.pb_GSE72326 <- step2(
  lm.pb_GSE72326, Control_ICU_sepsis - Healthy_control_of_sepsis
)
lm.pb_GSE72326 <- step3(lm.pb_GSE72326)
lm.pb_GSE72326@plots$step2$p.volcano$`Control_ICU_sepsis - Healthy_control_of_sepsis`
lm.pb_GSE72326@tables$step2$tops$`Control_ICU_sepsis - Healthy_control_of_sepsis`
```

## 交集: GSE13434 + GSE13734 + GSE23240 + GSE23275 + GSE24321 + GSE6906 + GSE7232 (BULK)

`r snap(venn.bulk, 0:1)`

```{r}
#' @meth {get_meth(venn.bulk)}
venn.bulk <- job_vennDEGs(
  "lm.pb_", exclude = c("lm.pb_GSE185263")
)
venn.bulk <- step1(venn.bulk, force_upset = TRUE)
wrap(venn.bulk@plots$step1$p.venn, 8.5, 5)
venn.bulk$degs_versus
feature(venn.bulk)
```

isThat <- unlist(feature(sr.sepsis)) %in% unlist(feature(lm.pb_GSE134347))
genesTDegs_nonVsSep <- unlist(feature(sr.sepsis))[isThat]
genesTDegs_nonVsSep

genesDiffTcells <- sr.sepsis@params$contrasts$gene
genesAlls <- collate("lm.pb_", function(x) x$normed_data$genes[[.guess_symbol(x)]], exclude = "lm.pb_GSE185263")
genesDiffTcells <- genesDiffTcells[ands(lapply(genesAlls, function(x) genesDiffTcells %in% x))]
genesDiffTcells


sets <- lapply(venn.bulk@object,
  function(obj) {
    genesDiffTcells %in% obj
  })
genesOrsTcells <- genesDiffTcells[ors(sets)]
genesOrsTcells

vis(sr.sepsis, "Cell_Type", mode = "sample")

## 使用外部数据验证 (VALID_GSE185263)

`r snap(dia.valid_GSE185263, "m")`

```{r}
dia.valid_GSE185263 <- asjob_diag(lm.pb_GSE185263)
dia.valid_GSE185263 <- step1(dia.valid_GSE185263)
dia.valid_GSE185263 <- map(dia.valid_GSE185263, dian.bulk)
#' @meth {get_meth(dia.valid_GSE185263)}
dia.valid_GSE185263@params$valid_results$lambda.min$p.roc
dia.valid_GSE185263@params$p.hp_valid
rm(dia.valid_GSE185263)
feature(dian.bulk)
```

## GEO 数据获取 (PB_GSE185263) (survival)

`r snap(geo.pb_GSE185263, 0:2)`

```{r}
geo.pb_GSE185263 <- job_geo("pb_GSE185263")
#' @meth {get_meth(geo.pb_GSE185263)}
geo.pb_GSE185263 <- step1(geo.pb_GSE185263)
geo.pb_GSE185263 <- step2(geo.pb_GSE185263)
rm(geo.pb_GSE185263, lm.pb_GSE185263)
metadata.pb_GSE185263 <- expect(geo.pb_GSE185263, geo_cols())
metadata.pb_GSE185263
```

## Limma 差异分析 (PB_GSE185263)

`r snap(lm.pb_GSE185263, 0:3)`

```{r}
lm.pb_GSE185263 <- asjob_limma(geo.pb_GSE185263, metadata.pb_GSE185263)
lm.pb_GSE185263 <- step1(lm.pb_GSE185263)
#' @meth {get_meth(lm.pb_GSE185263)}
lm.pb_GSE185263 <- step2(
  lm.pb_GSE185263, sepsis - healthy
)
lm.pb_GSE185263 <- step3(lm.pb_GSE185263)
```


sr.t_cell <- step6(
  sr.t_cell, "Peripheral", include = "\\bT\\b", keep_markers = 5,
  extra = c("PDCD1", "FOXP3", "CD4", "CTLA4", "IL2RA"), 
  exclude_pattern = NULL, exclude = "Naive"
)
