---
title: 
bibliography: '`r system.file("extdata", "library.bib", package = "utils.tool")`'
csl: '`r system.file("extdata", "nature.csl", package = "utils.tool")`'
reference-section-title: "Reference"
output:
  custom_docx_document2:
    reference_docx: '`r system.file("extdata", "bosai.docx", package = "utils.tool")`'
---


```{r include = F, eval = F}
info <- items(start = td("2024-11-21"), end = td("2025-03-21"), finish = td("2025-03-25"),
  id = "BSJF241107", client = "许冠华", inst = "",
  type = "生信协助",
  title = "脓毒症",
  save = ".items_support.rds"
)
show.ic(info)

order_publish.bosai("support.Rmd", "support_out.Rmd")
idname <- formatName.bosai("./support_out.docx")
order_packaging("./support_out.docx", idname = idname, external_file = NULL)
```

```{r include = F}
#| setup
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
autor_preset()
## the package are available at <https://github.com/shaman-yellow/utils.tool>
## if you want to run codes of this Rmarkdown,
## please install the package `utils.tool` and other related packages (run
## install.R)
options(savedir = list(figs = "Figure+Table", tabs = "Figure+Table"))
```

```{r eval = T, echo = F, results = "asis"}
set_cover.bosai(info)
```

```{r eval = T, echo = F, results = "asis"}
set_index()
```

# 分析流程 {#abstract}

1. 哪种类型T细胞起主要作用（参考一下这篇文章PMID：38291496）？
2. 筛选15个基因太多，能不能在缩减一下，主要看下这几个基因富集的信号通路或者生物学途径。

```{r}
dic(di("差异表达基因"),
  di("")
)

```

# 材料和方法 {#introduction}

```{r eval = T, echo = F, results = "asis"}
collate_details("meth")
```

# 分析结果 {#workflow}

## Seurat 细胞亚群分析 (T_CELL)

`r snap(sr.t_cell, 0:7)`
`r snap(sr.t_cell, "diff_contrasts")`

`r ref("T-CELL-UMAP-Clustering")`
`r ref("T-CELL-UMAP-Clustering")`
`r ref("T-CELL-significant-markers-of-cell-clusters")`
`r ref("Unnamed-1")`
`r ref("T-CELL-Marker-Validation")`
`r ref("T-CELL-SCSA-Cell-type-annotation")`
`r ref("T-CELL-The-Cell-Sample")`
`r ref("T-CELL-violing-plot-of-expression-level-feas")`
`r ref("T-CELL-dimension-plot-of-expression-level-feas")`
`r ref("T-CELL-DEGs-of-the-contrasts")`
<!-- LEGEND_END -->

```{r}
sr.sepsis <- readRDS("./sr.sepsis.4.rds")
sr.sepsis

sr.t_cell <- asjob_seurat_sub(sr.sepsis, Cell_Type == "T")
sr.t_cell <- step1(sr.t_cell)
sr.t_cell <- step2(sr.t_cell)
sr.t_cell <- step3(sr.t_cell, 1:15, 1.2)
sr.t_cell@plots$step3$p.umap
sr.t_cell <- step4(sr.t_cell, "")
set_remoteRun.bosai()
sr.t_cell <- set_remote(sr.t_cell)
sr.t_cell <- step5(sr.t_cell, 5)
sr.t_cell@tables$step5$all_markers
sr.t_cell@plots$step5$p.toph

t_cell_markers <- list(
  CD4_T = c("CD4"), # Specific combination: CD3D+CD4+eliminates monocyte interference
  CD8_T = c("CD8A", "CD8B"),        # Double CD8 chain labeling to avoid crossing with NK cells
  Non_classical = c("TRDC", "TRGC1")  # Combined labeling of gamma delta T and NKT
)
ref.markers <- as_df.lst(t_cell_markers, "cell", "markers")
ref.markers

sr.t_cell@step <- 5L
sr.t_cell <- step6(
  sr.t_cell, "blood", ref.markers, keep_markers = 4, 
  soft = FALSE, show = c("CD3D", "CD3E"),
  reset = c("Unknown" = "CD4-CD8- T Cell", "CD8_T" = "CD8+ T Cell")
)
sr.t_cell@plots$step6$p.markers
sr.t_cell@plots$step6$p.map_scsa

sr.t_cell <- mutate(
  sr.t_cell, Cell_Sample = as_type_group(scsa_cell, orig.ident)
)
p.tcell <- vis(sr.t_cell, "scsa_cell", mode = "sample")
p.tcell

dian.bulk <- readRDS("./dian.bulk.6.rds")
feature(dian.bulk)

sr.t_cell <- focus(sr.t_cell, feature(dian.bulk)[[1]], "Cell_Sample", name = "feas")
wrap(sr.t_cell@params$focus_feas$p.vln, 14, 12)
sr.t_cell@params$focus_feas$p.dim

sr.t_cell <- diff(
  sr.t_cell, "Cell_Sample", pattern_contrasts(
    sr.t_cell@object@meta.data$Cell_Sample, Sepsis - Control
  )
)
sr.t_cell@params$contrasts
```


```{r eval = T, echo = F, results = "asis"}
#| T-CELL-UMAP-Clustering
autor(sr.t_cell@plots$step3$p.umap)
```


```{r eval = T, echo = F, results = "asis"}
#| T-CELL-significant-markers-of-cell-clusters
autor(sr.t_cell@tables$step5$all_markers)
```



```{r eval = T, echo = F, results = "asis"}
#| T-CELL-Marker-Validation
autor(sr.t_cell@plots$step6$p.markers)
```


```{r eval = T, echo = F, results = "asis"}
#| T-CELL-SCSA-Cell-type-annotation
autor(sr.t_cell@plots$step6$p.map_scsa)
```


```{r eval = T, echo = F, results = "asis"}
#| T-CELL-The-Cell-Sample
autor(p.tcell)
```


```{r eval = T, echo = F, results = "asis"}
#| T-CELL-violing-plot-of-expression-level-feas
autor(wrap(sr.t_cell@params$focus_feas$p.vln, 14, 12))
```


```{r eval = T, echo = F, results = "asis"}
#| T-CELL-dimension-plot-of-expression-level-feas
autor(sr.t_cell@params$focus_feas$p.dim)
```


```{r eval = T, echo = F, results = "asis"}
#| T-CELL-DEGs-of-the-contrasts
autor(sr.t_cell@params$contrasts)
```

# 总结 {#conclusion}

对 T Cell 亚群分析，主要鉴定到 3 种亚群，见`r ref("T-CELL-SCSA-Cell-type-annotation")` 
对 15 个基因在 T 细胞中的表达量分析  (`r ref("T-CELL-dimension-plot-of-expression-level-feas")`，
`r ref("T-CELL-violing-plot-of-expression-level-feas")`) 
发现 PRF1 为高表达，且集中表达于 CD8+ T 细胞，此外， Sepsis_vs_Control 差异分析也分析，
PRF1 在 CD8+ T 中差异表达 (`r ref("T-CELL-DEGs-of-the-contrasts")`)。

