
### GSE200020: RNA-sequencing of pheripheral blood isolated cDC2s from patients with primary Sjögren’s syndrome (pSS; n=23), non-Sjögren’s sicca (nSS; n=15), and healthy controls (HC; n=18).

- pheripheral blood

```{r eval = T, echo = F, results = "asis"}
#| meta1
autor(ge1@params$prods)
```

```{r eval = T, echo = F, results = "asis"}
#| metadata-of-used-sample-of-GSE200020
autor(, key = "group.ch1")
```

```{r}
ge1 <- job_geo("GSE200020")
ge1 <- step1(ge1)
ge1 <- step2(ge1)
```

```{r}
mart <- new_biomart()

counts <- fxlsx("./GSE200020/GSE200020_normalized_gene_counts_VST_matrix_Discovery.xlsx")
genes <- filter_biomart(mart, general_attrs(), "ensembl_gene_id", counts$X1)
genes <- relocate(genes, 1, hgnc_symbol)
metadata <- group_strings(ge1@params$guess$title, c(control = "^HC", disease = "pSS"), "sample")
metadata <- mutate(metadata, sample = stringr::str_extract(sample, "^[^ ]+"))

lm1 <- job_limma(new_dge(metadata, counts, genes))
lm1@step <- 1L
lm1 <- step2(lm1, disease - control)
```

### GSE199868: RNA-sequencing of pheripheral blood isolated CD19+ B cells from patients with primary Sjögren’s syndrome (pSS; n=14), non-Sjögren’s sicca (nSS; n=11), and healthy controls (HC; n=13).

- CD19+ B cells

```{r}
ge2 <- job_geo("GSE199868")
ge2 <- step1(ge2)
ge2 <- step2(ge2)
```

### GSE194234: RNA sequencing of 7 pSS patients and 6 healthy controls

Total RNA of neutrophils was extracted using TRIzol reagent (Invitrogen, USA) and stored at −80 °C for subsequent RNA sequencing (Novogene, China)

- neutrophils

```{r}
ge3 <- job_geo("GSE194234")
ge3 <- step1(ge3)
ge3 <- step2(ge3)
```

### GSE173635: FACS sorted CCR9+, CXCR5+ and CCR9-CXCR5- Th cells from peripheral blood of n=7 pSS patients and n=7 HC were analyzed using RNA sequencing

- CCR9+, CXCR5+ and CCR9-CXCR5- Th cells

```{r}
ge4 <- job_geo("GSE173635")
ge4 <- step1(ge4)
ge4 <- step2(ge4)

ge4@params$prods
```

### GSE173670: RNA-sequencing of pheripheral blood isolated CD14+ monocytes from patients with primary Sjögren’s syndrome (pSS; n=14) , non-Sjögren’s sicca (nSS; n=8), and healthy controls (HC; n=14).

- pheripheral blood isolated CD14+ monocytes

### GSE171896: minor salivary glands (MSGs) from 36 patients with ILD-pSS and 128 patients with non-ILD-pSS

- minor salivary glands (MSGs)
