---
title: 
bibliography: '`r system.file("extdata", "library.bib", package = "utils.tool")`'
csl: '`r system.file("extdata", "nature.csl", package = "utils.tool")`'
reference-section-title: "Reference"
link-citations: true
output:
  bookdown::pdf_document2:
    # pandoc_args: [
      # "--filter", "pandoc-fignos",
      # "--filter", "pandoc-tablenos"
    # ]
    keep_tex: true
    keep_md: true
    toc: false
    # toc_depth: 4
    latex_engine: xelatex
header-includes:
  \usepackage{tikz}
  \usepackage{auto-pst-pdf}
  \usepackage{pgfornament}
  \usepackage{pstricks-add}
  \usepackage{caption}
  \captionsetup{font={footnotesize},width=6in}
  \renewcommand{\dblfloatpagefraction}{.9}
  \makeatletter
  \renewenvironment{figure}
  {\def\@captype{figure}}
  \makeatother
  \@ifundefined{Shaded}{\newenvironment{Shaded}}
  \@ifundefined{snugshade}{\newenvironment{snugshade}}
  \renewenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
  \definecolor{shadecolor}{RGB}{230,230,230}
  \usepackage{xeCJK}
  \usepackage{setspace}
  \setstretch{1.3} 
  \usepackage{tcolorbox}
  \setcounter{secnumdepth}{4}
  \setcounter{tocdepth}{4}
  \usepackage{wallpaper}
  \usepackage[absolute]{textpos}
  \tcbuselibrary{breakable}
  \renewenvironment{Shaded}
  {\begin{tcolorbox}[colback = gray!10, colframe = gray!40, width = 16cm,
    arc = 1mm, auto outer arc, title = {R input}]}
  {\end{tcolorbox}}
  \usepackage{titlesec}
  \titleformat{\paragraph}
  {\fontsize{10pt}{0pt}\bfseries} {\arabic{section}.\arabic{subsection}.\arabic{subsubsection}.\arabic{paragraph}} {1em} {} []

---


```{r include = F, eval = F}
deparse_mail()
info <- items(belong = odate(06), eval = ic(), lock = T, id = "no", class = "-")
show.ic(info)

order_publish()
idname <- order_packaging()
```

```{r include = F}
#| setup
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
autor_preset(T)
## the package are available at <https://github.com/shaman-yellow/utils.tool>
## if you want to run codes of this Rmarkdown,
## please install the package `utils.tool` and other related packages (run
## install.R)
options(savedir = list(figs = "Figure+Table", tabs = "Figure+Table"))
```

```{r eval = T, echo = F, results = "asis"}
# set_cover(info$title)
```

```{r eval = T, echo = F, results = "asis"}
set_index()
```

# 摘要 {#abstract}

```{r}
dic(di("差异表达基因", "Differential Expressed Genes", "DEGs"),
  di("非酒精性脂肪肝")
)

# DEGs: Differential Expressed Genes 差异表达基因
# NFLD: Nonalcoholic fatty liver disease 非酒精性脂肪肝
```



# 前言 {#introduction}

# 材料和方法 {#methods}

## 材料

```{r eval = T, echo = F, results = "asis"}
auto_material()
```

## 方法

```{r eval = T, echo = F, results = "asis"}
auto_method()
```

# 分析结果 {#results}

# 结论 {#dis}

# 附：分析流程 {#workflow}

## 成分

- Aconitic acid
- Dianthoside
- Allo Maltol
- 6-Hydroxycoumarin
- Homovanillyl alcohol 4-O-glucoside
- Epicatechin
- Isoquercetin
- Berberine
- Quinic acid
- 2-Furoic acid
- Adoxosidic acid
- Neochlorogenic acid
- 3-O-Feruloylquinic acid
- Rutin
- Quercetin
- Isorhamnetin
- Gingerol

```{r}
cpds <- c("Aconitic acid", "Dianthoside", "Allo Maltol", "6-Hydroxycoumarin", "Homovanillyl alcohol 4-O-glucoside",
  "Epicatechin", "Isoquercetin", "Berberine", "Quinic acid", "2-Furoic acid", "Adoxosidic acid",
  "Neochlorogenic acid", "3-O-Feruloylquinic acid", "Rutin", "Quercetin",
  "Isorhamnetin", "Gingerol")
infoCpds <- PubChemR::get_cids(cpds)
infoCpds <- dplyr::distinct(infoCpds, Identifier, .keep_all = T)
if (!identical(nrow(infoCpds), length(cpds))) {
  message("Not Found some compounds.")
}
infoCpds <- dplyr::mutate(infoCpds, CID = as.integer(CID))
infoCpds
```

```{r}
pub <- job_pubchemr(nl(infoCpds$Identifier, infoCpds$CID, F))
pub <- step1(pub)
```

## 成分靶点

```{r}
sup <- asjob_superpred(pub)
sup <- step1(sup)
sup@tables$step1$targets
```


```{r eval = T, echo = F, results = "asis"}
#| Targets-predicted-by-Super-Pred
autor(sup@tables$step1$targets)
```

## 成分靶点网络

```{r}
hb <- do_herb(pub, sup)
hb@plots$step3$p.pharm
```


```{r eval = T, echo = F, results = "asis"}
#| Network-pharmacology-visualization
autor(hb@plots$step3$p.pharm)
```

## 疾病靶点

```{r}
gm <- job_gmix("Nonalcoholic fatty liver disease", "nonalcoholic")
gm <- step1(gm)
gm <- step2(gm, NULL, 1, 3, restrict = T)
gm@tables$step2$t.genecard
gm@plots$step2$p.cols
```

```{r eval = T, echo = F, results = "asis"}
#| GeneCards-used-data
autor(gm@tables$step2$t.genecard)
```


```{r eval = T, echo = F, results = "asis"}
#| Overall-targets-number-of-datasets
autor(gm@plots$step2$p.cols)
```

## 成分-疾病-靶点

```{r}
hb <- map(hb, gm@params$lst.genes, name = "dis", less.label = F)
hb@params$p.pharm2dis
hb@params$p.venn2dis
```

```{r eval = T, echo = F, results = "asis"}
#| Network-pharmacology-with-disease
autor(hb@params$p.pharm2dis)
```


```{r eval = T, echo = F, results = "asis"}
#| Targets-intersect-with-targets-of-diseases
autor(hb@params$p.venn2dis)
```

## 分子对接

```{r}
dockLayout <- dplyr::select(hb@params$p.pharm2dis$.data, -1)
dockLayout <- map(dockLayout, "Ingredient.name", infoCpds, "Identifier", "CID", col = "CID")
dockLayout

vn <- job_vina(.layout = dockLayout)
vn <- step1(vn)
vn <- step2(vn)
vn <- step3(vn)
vn <- set_remote(vn)
vn <- step4(vn)
vn <- step5(vn)
wrap(vn@plots$step5$p.res_vina, 7, 9.5)
vn@tables$step5$res_dock
vn <- step6(vn, top = 3)
vn@plots$step6$Top1_643757_into_1tqn
vn@plots$step6$Top2_99477_into_2dn8
vn@plots$step6$Top3_5316639_into_4cgv
vn <- step7(vn)
vn@plots$step7$Top1_643757_into_1tqn
vn@plots$step7$Top2_99477_into_2dn8
vn@plots$step7$Top3_5316639_into_4cgv
```

```{r eval = T, echo = F, results = "asis"}
#| Overall-combining-Affinity
autor(wrap(vn@plots$step5$p.res_vina, 7, 9.5))
```


```{r eval = T, echo = F, results = "asis"}
#| Affinity-data
autor(vn@tables$step5$res_dock)
```

### 对接可视化

```{r eval = T, echo = F, results = "asis"}
#| Docking-643757-into-1tqn
autor(vn@plots$step6$Top1_643757_into_1tqn)
```


```{r eval = T, echo = F, results = "asis"}
#| Docking-99477-into-2dn8
autor(vn@plots$step6$Top2_99477_into_2dn8)
```


```{r eval = T, echo = F, results = "asis"}
#| Docking-5316639-into-4cgv
autor(vn@plots$step6$Top3_5316639_into_4cgv)
```

### 对接细节可视化

```{r eval = T, echo = F, results = "asis"}
#| Docking-643757-into-1tqn-detail
autor(vn@plots$step7$Top1_643757_into_1tqn)
```


```{r eval = T, echo = F, results = "asis"}
#| Docking-99477-into-2dn8-detail
autor(vn@plots$step7$Top2_99477_into_2dn8)
```


```{r eval = T, echo = F, results = "asis"}
#| Docking-5316639-into-4cgv-detail
autor(vn@plots$step7$Top3_5316639_into_4cgv)
```

