---
---

```{r include = F}
#| setup
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
autor_preset()
## the package are available at <https://github.com/shaman-yellow/utils.tool>
## if you want to run codes of this Rmarkdown,
## please install the package `utils.tool` and other related packages (run
## install.R)
options(savedir = list(figs = "Figure+Table", tabs = "Figure+Table"))
```

```{r eval = T, echo = F, results = "asis"}
set_index()
```

# 题目

# 摘要 {#abstract}

# 前言 {#introduction}

CKD 与患癌症风险之间的联系尚未明确。尽管多项研究观察到需要透析或肾移植的 ESRD 患者患癌症的风险较高，但不太严重的肾脏疾病是否与癌症相关仍知之甚少[@OnconephrologyRosner2021; @CkdAndTheRisLowran2014; @CancerRiskAndKitchl2022]。

肾癌流行病学[@EpidemiologyOfBukavi2022]

CKD 和肾癌[@RenalCellCancSaly2021]

Cancer Risk and Mortality in Patients With Kidney Disease: Cancer risk was increased in mild to moderate CKD and among transplant recipients[@CancerRiskAndKitchl2022]

# 研究设计流程图 {#route}

TCGA 突变数据
TCGA 转录数据
基因共表达
免疫浸润水平
生存分析
timeROC
单细胞数据验证

```{r}
#| route
route <- as_network(
  list("RNA_seq_data:Preprocess",
    ), "tree"
)
p.route <- flowChart(route, 1.1, 1)
```

```{r, eval = T, echo = F, fig.width = 10, fig.height = 7, fig.cap = NULL}
p.route
```

# 材料和方法 {#methods}

```{r}
lite_cancer <- esearch.mj("cancer prediction")
lite_cancer %>% select(.id, Title) %>% print(n = 100)
```

# 分析结果 {#results}

# 结论 {#dis}

# 附：分析流程

## 肾癌 (TCGA-KIRC)

### 转录组（Transcriptome Profiling）

```{r}
tc <- job_tcga("TCGA-KIRC")
tc <- step1(tc)
tc <- step2(tc)
tc <- step3(tc)
tc <- clear(tc)

lm <- asjob_limma(tc)
```

### 基因组（Mutation data）

```{r}
# https://www.bioconductor.org/packages/release/bioc/vignettes/TCGAbiolinks/inst/doc/mutation.html
```

## 慢性肾病

```{r}
# https://www.tokushukai.or.jp/cn/treatment/internal/nephrology/jinzoubyou_jinfuzen.php
```

### GSE60861: An integrative analysis of renal miRNA- and mRNA-expression signatures in progressive chronic kidney disease

## 血管性疾患

### 高血压性肾炎（hypertensive nephropathy）
- GSE210898: Single-cell RNA transcriptomics of hypertensive nephropathy patients

## （原发性）肾小球性疾患

### IgA 肾病 (IgA Nephropathy)
- GSE145652, RNA-seq
- GSE175759, RNA-seq

### 膜性肾病 (idiopathic membranous nephropathy)
- GSE216841, RNA-seq
- GSE241302, scRNA
- GSE175759, RNA-seq

### 微小病变肾病 (Minimal change disease)
- GSE216841, RNA-seq
- GSE175759, RNA-seq

## （继发性）肾小球性疾患

### 糖尿病肾病 (Diabetic kidney disease)
- GSE175759, RNA-seq
- GSE199838, RNA-seq
- GSE217709, RNA-seq

### 狼疮性肾炎 (lupus nephritis)
- GSE175759, RNA-seq
- GSE157293, RNA-seq

