---
---

```{r include = F, eval = F}
info <- items(start = td("2026-02-19"), end = td("2026-02-19"), finish = td("2026-02-19"),
  id = "test", client = "", inst = "",
  type = "index",
  title = "",
  save = ".items_index.rds"
)
show.ic(info)

order_publish.complex("index.Rmd", "index_out.Rmd")
idname <- formatName.complex("./index_out.docx")
order_packaging("./index_out.docx", idname = idname, external_file = NULL)
```

```{r include = F}
#| setup
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
autor_preset()
## the package are available at <https://github.com/shaman-yellow/utils.tool>
## if you want to run codes of this Rmarkdown,
## please install the package `utils.tool` and other related packages (run
## install.R)
options(savedir = list(figs = "Figure+Table", tabs = "Figure+Table"))
```

```{r eval = T, echo = F, results = "asis"}
set_cover.complex(info)
```

```{r eval = T, echo = F, results = "asis"}
set_index()
```

# 分析流程 {#abstract}

```{r}
dic(di("差异表达基因"),
  di("")
)

```

# 材料和方法 {#introduction}

```{r eval = T, echo = F, results = "asis"}
collate_details("meth")
```

# 分析结果 {#workflow}

## BATMAN 网络药理学 (XIAOYU)

`r snap(bat.xiaoyu, 0:3)`

`r ref("Intersection-of-herbs-compounds")` 
`r ref("Intersection-of-herbs-all-targets")` 
`r ref("Herbs-compounds-and-targets")` 

```{r}
herbs <- c("黄芪", "川牛膝", "桃仁", "地龙", "大黄", "车前草")
bat.xiaoyu <- job_batman(herbs)
#' @meth {get_meth(bat.xiaoyu)}
bat.xiaoyu <- step1(bat.xiaoyu, filter.hob = TRUE)
bat.xiaoyu <- step2(bat.xiaoyu, cutoff = .5)
bat.xiaoyu <- step3(bat.xiaoyu)

bat.xiaoyu@plots$step3$p.herbs_compounds
bat.xiaoyu@plots$step3$p.herbs_targets
bat.xiaoyu@params$easyRead

```



## GeneCards 基因获取 (DN)

`r snap(gn.dn, 0:1)`

`r ref("CKD-disease-related-targets-from-GeneCards")`

```{r}
gn.dn <- job_genecard("Diabetic nephropathy")
gn.dn <- step1(gn.dn, 1)
#' @meth {get_meth(gn.dn)}
gn.dn@tables$step1$t.genecards

```


```{r eval = T, echo = F, results = "asis"}
#| CKD-disease-related-targets-from-GeneCards
autor(gn.dn@tables$step1$t.genecards)
```

## Network 中药-成分-疾病-靶点网络 (XIAOYU)

`r snap(bat.xiaoyu, "m")`

`r ref("Targets-intersect-with-related-targets-dis")` 
`r ref("Network-pharmacology-with-filtered-type-original-data-dis")` 
`r ref("Network-pharmacology-with-filtered-type-dis")` 

```{r}
bat.xiaoyu <- map(bat.xiaoyu, feature(gn.dn))
bat.xiaoyu@params$p.venn2dis
bat.xiaoyu@params$t.pharm2dis
wrap(bat.xiaoyu@params$p.pharm2dis, 13, 10)
```


```{r eval = T, echo = F, results = "asis"}
#| Targets-intersect-with-related-targets-dis
autor(bat.xiaoyu@params$p.venn2dis)
```


```{r eval = T, echo = F, results = "asis"}
#| Network-pharmacology-with-filtered-type-original-data-dis
autor(bat.xiaoyu@params$t.pharm2dis)
```


```{r eval = T, echo = F, results = "asis"}
#| Network-pharmacology-with-filtered-type-dis
autor(wrap(bat.xiaoyu@params$p.pharm2dis, 13, 10))
```

## EpiFactors 表观遗传调控因子数据获取 (M6A)

`r snap(epi.m6a, 0:1)`

`r ref("M6A-all-protein-of-epigenetic-regulators")` 

```{r}
epi.m6a <- job_epifactor()
#' @meth {get_meth(epi.m6a)}
epi.m6a <- step1(epi.m6a)
epi.m6a <- filter(epi.m6a)
epi.m6a@tables$step1$protein
feature(epi.m6a)
```


```{r eval = T, echo = F, results = "asis"}
#| M6A-all-protein-of-epigenetic-regulators
autor(epi.m6a@tables$step1$protein)
```

## 交集: All_RNA_methylation + DN_related (M6A)

`r snap(venn.m6a, 0:1)`

`r ref("Intersection-of-All-RNA-methylation-with-DN-related")` 

```{r}
venn.m6a <- job_venn(
  All_RNA_methylation = feature(epi.m6a), DN_related = feature(gn.dn)
)
venn.m6a <- step1(venn.m6a)
venn.m6a@plots$step1$p.venn
```


```{r eval = T, echo = F, results = "asis"}
#| Intersection-of-All-RNA-methylation-with-DN-related
autor(venn.m6a@plots$step1$p.venn)
```

## Network 中药-成分-疾病-甲基靶点网络 (m6a)


`r ref("Network-pharmacology-with-filtered-type-m6a")` 
`r ref("Network-pharmacology-with-filtered-type-original-data-m6a")` 

```{r}
bat.xiaoyu <- map(
  bat.xiaoyu, feature(venn.m6a), name = "m6a", less.label = FALSE
)
wrap(bat.xiaoyu@params$p.pharm2m6a, 7, 4.5)
bat.xiaoyu@params$t.pharm2m6a
```

```{r eval = T, echo = F, results = "asis"}
#| Network-pharmacology-with-filtered-type-m6a
autor(wrap(bat.xiaoyu@params$p.pharm2m6a, 7, 4.5))
```


```{r eval = T, echo = F, results = "asis"}
#| Network-pharmacology-with-filtered-type-original-data-m6a
autor(bat.xiaoyu@params$t.pharm2m6a)
```

## AutoDock vina 分子对接 (M6A)

`r snap(vina.m6a, 0:7)`

`r ref("M6A-All-combining-Affinity-data")` 
`r ref("M6A-Overall-combining-Affinity")` 
`r ref("Docking-243-into-5il2")` 
`r ref("Docking-34755-into-5il2")` 
`r ref("Docking-34755-into-5il2-b")` 
`r ref("Docking-243-into-5il2-detail")` 
`r ref("Docking-34755-into-5il2-detail")` 
`r ref("Docking-34755-into-5il2-b-detail")` 

注：METTL3 与 METTL14 的蛋白结构常见为复合体 (METTL3-METTL14 complex, PDB:5IL2)，

```{r}
vina.m6a <- asjob_vina(bat.xiaoyu, feature(venn.m6a))
#' @meth {get_meth(vina.m6a)}
vina.m6a <- step1(vina.m6a, custom_pdbs = c("METTL14" = "5IL2"))
vina.m6a <- step2(vina.m6a)
vina.m6a <- step3(vina.m6a)
vina.m6a <- step4(vina.m6a)
vina.m6a <- step5(vina.m6a)
vina.m6a@tables$step5$res_dock
wrap(vina.m6a@plots$step5$p.res_vina, 8, 3)

vina.m6a <- step6(vina.m6a)
vina.m6a@plots$step6$Top1_243_into_5il2
vina.m6a@plots$step6$Top2_34755_into_5il2
vina.m6a@plots$step6$Top3_34755_into_5il2_b

vina.m6a <- step7(vina.m6a)
vina.m6a@plots$step7$Top1_243_into_5il2
vina.m6a@plots$step7$Top2_34755_into_5il2
vina.m6a@plots$step7$Top3_34755_into_5il2_b
```


```{r eval = T, echo = F, results = "asis"}
#| M6A-All-combining-Affinity-data
autor(vina.m6a@tables$step5$res_dock)
```


```{r eval = T, echo = F, results = "asis"}
#| M6A-Overall-combining-Affinity
autor(wrap(vina.m6a@plots$step5$p.res_vina, 8, 3))
```


```{r eval = T, echo = F, results = "asis"}
#| Docking-243-into-5il2
autor(vina.m6a@plots$step6$Top1_243_into_5il2)
```


```{r eval = T, echo = F, results = "asis"}
#| Docking-34755-into-5il2
autor(vina.m6a@plots$step6$Top2_34755_into_5il2)
```


```{r eval = T, echo = F, results = "asis"}
#| Docking-34755-into-5il2-b
autor(vina.m6a@plots$step6$Top3_34755_into_5il2_b)
```


```{r eval = T, echo = F, results = "asis"}
#| Docking-243-into-5il2-detail
autor(vina.m6a@plots$step7$Top1_243_into_5il2)
```


```{r eval = T, echo = F, results = "asis"}
#| Docking-34755-into-5il2-detail
autor(vina.m6a@plots$step7$Top2_34755_into_5il2)
```


```{r eval = T, echo = F, results = "asis"}
#| Docking-34755-into-5il2-b-detail
autor(vina.m6a@plots$step7$Top3_34755_into_5il2_b)
```

## CatRAPID omics RBP 预测 (RBP)

`r snap(catr.rbp, 0:3)`

```{r}
catr.rbp <- job_catr(c("METTL3", "METTL14"), "MEG3")
catr.rbp <- step1(catr.rbp)
#' @meth {get_meth(catr.rbp)}
catr.rbp <- step2(catr.rbp)
catr.rbp@tables$step2$top

```

```{r eval = T, echo = F, results = "asis"}
#| RBP-RBP-top-interaction
autor(catr.rbp@tables$step2$top)
```

## m6A-Atlas m6A 数据获取 (MEG3)

`r snap(m6a.meg3, 0:1)`

```{r}
m6a.meg3 <- job_m6a()
#' @meth {get_meth(m6a.meg3)}
m6a.meg3 <- step1(m6a.meg3, "MEG3")
m6a.meg3@tables$step1$t.data$HighResolution
```


```{r eval = T, echo = F, results = "asis"}
#| MEG3-HighResolution-m6A-Atlas-search-results
autor(m6a.meg3@tables$step1$t.data$HighResolution)
```


# 总结 {#conclusion}

