---
title: 
bibliography: '`r system.file("extdata", "library.bib", package = "utils.tool")`'
csl: '`r system.file("extdata", "nature.csl", package = "utils.tool")`'
reference-section-title: "Reference"
link-citations: true
output:
  bookdown::pdf_document2:
    # pandoc_args: [
      # "--filter", "pandoc-fignos",
      # "--filter", "pandoc-tablenos"
    # ]
    keep_tex: true
    keep_md: true
    toc: false
    # toc_depth: 4
    latex_engine: xelatex
header-includes:
  \usepackage{caption}
  \captionsetup{font={footnotesize},width=6in}
  \renewcommand{\dblfloatpagefraction}{.9}
  \makeatletter
  \renewenvironment{figure}
  {\def\@captype{figure}}
  \makeatother
  \@ifundefined{Shaded}{\newenvironment{Shaded}}
  \@ifundefined{snugshade}{\newenvironment{snugshade}}
  \renewenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
  \definecolor{shadecolor}{RGB}{230,230,230}
  \usepackage{xeCJK}
  \usepackage{setspace}
  \setstretch{1.3} 
  \usepackage{tcolorbox}
  \setcounter{secnumdepth}{4}
  \setcounter{tocdepth}{4}
  \usepackage{wallpaper}
  \usepackage[absolute]{textpos}
  \tcbuselibrary{breakable}
  \renewenvironment{Shaded}
  {\begin{tcolorbox}[colback = gray!10, colframe = gray!40, width = 16cm,
    arc = 1mm, auto outer arc, title = {R input}]}
  {\end{tcolorbox}}
  \usepackage{titlesec}
  \titleformat{\paragraph}
  {\fontsize{10pt}{0pt}\bfseries} {\arabic{section}.\arabic{subsection}.\arabic{subsubsection}.\arabic{paragraph}} {1em} {} []

---


```{r include = F, eval = F}
deparse_mail()
info <- items(belong = odate(3), eval = ic(0, 1, 1, 1, 0))

order_publish()
idname <- order_packaging()
```

```{r include = F}
#| setup
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
autor_preset()
## the package are available at <https://github.com/shaman-yellow/utils.tool>
## if you want to run codes of this Rmarkdown,
## please install the package `utils.tool` and other related packages (run
## install.R)
options(savedir = list(figs = "Figure+Table", tabs = "Figure+Table"))
```

```{r eval = T, echo = F, results = "asis"}
set_cover(info$title)
```

```{r eval = T, echo = F, results = "asis"}
set_index()
```

# 摘要 {#abstract}

```{r}
dic(di("差异表达基因", "Differential Expressed Genes", "DEGs"),
  di("自身免疫性肠病")
)

# DEGs: Differential Expressed Genes 差异表达基因
# AE: autoimmune enteropathy 自身免疫性肠病
```

## 需求

复方组成：

The decoction consisted of 30 g astragalus membranaceus (huangqi黄芪3), 10 g polygonatum odoratum (yuzu玉竹), 6 g scolopendra subspinipes mutilans (tianlong蜈蚣4), 6 g pberetima (dilong地龙), 20 g solanum nigrum (longkui龙葵5), 20 g herbahedyotis (baihushecao白花蛇舌草), 20 g semen coicis (yiyiren薏苡仁), 6 g euphorbia helioscopia (zeqi泽漆), 10 g curcuma longa (eshu莪术6) and 6 g tendril-leaved fritillary bulb (chuanbei川贝母).

疾病：自身免疫性肠病

## 结果

- 网络药理图见 Fig. \@ref(fig:Network-pharmacology-with-disease)
- 通路聚焦见，Fig. \@ref(fig:Hsa04068-visualization) (SIRT1 相关) 


# 前言 {#introduction}

# 材料和方法 {#methods}

## 材料

```{r eval = T, echo = F, results = "asis"}
auto_material()
```

## 方法

```{r eval = T, echo = F, results = "asis"}
auto_method()
```

# 分析结果 {#results}

# 结论 {#dis}

# 附：分析流程 {#workflow}

## 网络药理学

### 成分靶点

```{r eval = T, echo = F, results = "asis"}
#| Herbs-information
autor(hb@params$herbs_info)
```

```{r eval = T, echo = F, results = "asis"}
#| Components-of-Herbs
autor(hb@tables$step1$herbs_compounds, key = "Ingredient.name")
```

```{r eval = T, echo = F, results = "asis"}
#| intersection-of-all-compounds
autor(wrap(hb@plots$step3$p.herbs_compounds, 12))
```

### 疾病

```{r eval = T, echo = F, results = "asis"}
#| Overall-targets-number-of-datasets
autor(gm@plots$step2$p.cols)
```

```{r eval = T, echo = F, results = "asis"}
#| GeneCards-used-data
autor(gm@tables$step2$t.genecard)
```

### 成分-靶点-疾病

```{r eval = T, echo = F, results = "asis"}
#| Targets-intersect-with-targets-of-diseases
autor(hb@params$p.venn2dis)
```

```{r eval = T, echo = F, results = "asis"}
#| Network-pharmacology-with-disease
autor(hb@params$p.pharm2dis)
```

### 富集分析

```{r eval = T, echo = F, results = "asis"}
#| KEGG-enrichment
autor(en@plots$step1$p.kegg$ids)
```

```{r eval = T, echo = F, results = "asis"}
#| GO-enrichment
autor(en@plots$step1$p.go$ids)
```

### 富集结果筛选

以 SIRT1 筛选显著富集的通路

```{r eval = T, echo = F, results = "asis"}
#| Filter-by-match-genes
autor(t.sirt1)
```

```{r eval = T, echo = F, results = "asis"}
#| Hsa04068-visualization
autor(en@plots$step2$p.pathviews$hsa04068)
```

```{r}
herbs <- c("黄芪", "玉竹", "蜈蚣", "地龙", "龙葵", "白花蛇舌草", "薏苡仁", "泽漆", "莪术", "川贝母")

hb <- job_herb(herbs)
hb@params$herbs_info %<>% dplyr::distinct(Herb_cn_name, .keep_all = T)
hb@params$herbs_info
hb <- step1(hb)
hb@tables$step1$herbs_compounds
hb <- step2(hb)
hb@tables$step2$compounds_targets
dplyr::filter(hb@tables$step2$compounds_targets, grpl(Target.name, "SIRT1|IL-6"))

hb <- step3(hb)
hb@plots$step3$p.pharm

gm <- job_gmix("autoimmune colitis", "autoimmune|enteropathy")
gm <- step1(gm)
gm@params$lst_dis
gm <- step2(gm, 2, 17, 4)
gm@plots$step2$p.cols
gm@tables$step2$t.genecard

hb <- map(hb, gm@params$lst.genes, c("SIRT1", "IL6"), less.label = T)
hb@params$p.pharm2dis
hb@params$p.venn2dis

en <- job_enrich(hb@params$p.venn2dis$ins)
en <- step1(en)
en <- step2(en, "hsa04068")
en@plots$step2$p.pathviews$hsa04068

t.sirt1 <- filter(en, "^SIRT1$")
t.sirt1
```

