---
---

```{r include = F}
#| setup
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
autor_preset()
## the package are available at <https://github.com/shaman-yellow/utils.tool>
## if you want to run codes of this Rmarkdown,
## please install the package `utils.tool` and other related packages (run
## install.R)
options(savedir = list(figs = "Figure+Table", tabs = "Figure+Table"))
```

```{r eval = T, echo = F, results = "asis"}
set_index()
```

# 题目

待定（根据实际分析）

# 摘要 {#abstract}

(方案设计)

方向：皮肤科，特应性皮炎（Atopic Dermatitis，AD）[@MolecularMechaSroka2021; @FromEmollientsSalvat2021]
分值：5分+

AD 涉及的因素较多（epidermal barrier dysfunction, host genetics, environmental factors, and immune perturbations[@FromEmollientsSalvat2021]）。

AD 中调节皮肤屏障功能和免疫反应的潜在机制和关键分子已被揭示[@SkinBarrierAbYang2020]。

JAK-STAT signaling pathway in AD[@JakStatSignalHuang2022]

Biomarkers of AD[@BiomarkersInABakker2023]

Is Atopic Dermatitis Only a Skin Disease?[@IsAtopicDermaMesjas2023]

- 可用的 GEO 数据集
    - GSE224783, RNA-seq
    - GSE237920, RNA-seq
    - GSE184509, RNA-seq
    - GSE213849, scRNA-seq
    - GSE197023, ST, scRNA-seq
    - GSE222840, scRNA-seq
    - ...
- RNA-seq 数据分析
    - 差异分析
    - 富集分析[@ClusterprofilerWuTi2021]
    - 免疫浸润预测[@EstimatingTheBecht2016]
    - 基因共表达（WGCNA）[@WgcnaAnRPacLangfe2008]
    - ...
- 单细胞数据分析（或验证）
    - 细胞鉴定[@IntegratedAnalHaoY2021]（The pathology of AD is accompanied by an imbalance in immunity involving Th1, Th2, and Treg cells, culminating in alterations in Th1- and Th2-mediated immune responses and IgE-mediated hypersensitivity[@SkinBarrierAbYang2020]）
    - 差异分析
    - 拟时分析[@TheDynamicsAnTrapne2014]
    - 细胞通讯[@InferenceAndAJinS2021]
    - ...



# 前言 {#introduction}

# 研究设计流程图 {#route}

```{r}
#| route
route <- as_network(
  list("RNA_seq_data:Preprocess",
    ), "tree"
)
p.route <- flowChart(route, 1.1, 1)
```

```{r, eval = T, echo = F, fig.width = 10, fig.height = 7, fig.cap = NULL}
p.route
```

# 材料和方法 {#methods}

# 分析结果 {#results}

# 结论 {#dis}
