# Experimental record

## *E. ulmodes* dose

Pharmacopoeia (2020) dosage: 6 ~ 10 g

```{r, eval = T, echo = T}

library(dplyr)

group <- c("control", "model", "raw.eu", "pro.eu", "positive", "extra")

dose.meta <- data.table::data.table(No. = 1:length(group)) %>% 
  dplyr::mutate(group = group,
                drug = c("-", "-", "raw.eu", "pro.eu", "pos.drug", "MTA"),
                n = 15,
                low = ifelse(grepl("eu", drug), "5", "-"),
                medium = ifelse(grepl("eu", drug), "10", "-"),
                high = ifelse(grepl("eu", drug), "20", "-")) %>% 
  dplyr::as_tibble()
knitr::kable(dose.meta)

```

Known Variables

$$
\begin{aligned}
D_{base} &= 15\ (g) \\
w_{rat.weight} &= 400\ (g)\\
w_{hum.weight} &= 60, 000\ (g) \\
C_{cofficient} &= 6 \\
T_{times} &= 28\ (day) \\
n_{group.rat.number} &= 15 \\
M_{group.h.m.l} &= 2 \times (5 + 10 + 20) \\
&= 70 \ (multiple)
\end{aligned}
$$

Require *E. ulmoides* ($W_{eu}$):

$$
\begin{aligned}
W_{eu} &= D \times \frac{w_{rat.}}{w_{hum.}} \times C \times T \times n \times M \\
&= 17640 \ (g) \\
&= 17.640 \ (kg)
\end{aligned}
$$

## *E. ulmoides* processing and extracting

### Raw.eu

+ 10 kg *E. ulmoides*
+ ...

### Pro.eu

+ 10 kg *E. ulmodes*
+ 20 g of salt per 1 kg (2% salt)
+ Salt is dissolved in water in a ratio of 1:20 (20 g dissolve in 400 ml water)
+ Stir-fry over moderate fire, until shreds are broken and the surface is charred black

### Extract

+ Solvent: 70% Ethanol.
+ Ratio: E. ulmodes extract with 1:10 solvent.

```{r}
df <- data.table::data.table(
  reagent = c("salt (g)",
              "95% Ethanol (L)"), 
  amount = c(400, "NA")
)
df <- dplyr::as_tibble(df)
knitr::kable(df)
```
