

UniTmp: unified resources for transmembrane proteins

```{r eval = T, echo = F, results = "asis"}
#| UniTmp-data-of-htp-all
autor(ut@object)
```

```{r}
ut <- job_unitmp()
ut@object$transmembrane
```

### Necroptosis

坏死性凋亡信号通路在肿瘤发生发展、肿瘤坏死、肿瘤转移和肿瘤免疫反应中发挥作用；坏死性凋亡可能促进或抗肿瘤发生，具体取决于肿瘤的类型[@NecroptosisAndYanJ2022]。

```{r}
filter(sdb.dps, )
```

(((breast cancer) OR (colorectal cancer)) AND (Proteomics)) AND (Drug resistance)

Single-cell and spatial profiling identify three response trajectories to pembrolizumab and radiation therapy in triple negative breast cancer (PMID: 38194915)

Abemaciclib Is Effective in Palbociclib-Resistant Hormone Receptor-Positive Metastatic Breast Cancers
(PMID: 37384539)

```{r}


prr <- job_prr(exprDataBortezomib, "Cisplatin")
prr@params$p.drugQQ
prr <- step1(prr)
prr@plots$step1$p.cvOut
prr <- step2(prr)
prr@tables$step2$t.predict


tc.rna <- step3(tc, query = "RNA")
lm.rna <- asjob_limma(tc.rna)
lm.rna <- step1(lm.rna)
lm.rna@object$genes$gene_name %>% gname

tc.pr <- step3(tc, query = "protein", clinical.info = "drug")
tc.pr@params$metadata$drug_name


fun <- function() {
  data <- prr@tables$step2$t.predict
  fun2 <- function(n) {
    print("-----------")
    print(mean(data[data$kmeans_group == n, ][[2]]))
  }
  fun2(1)
  fun2(2)
  fun2(3)
}
fun()
 
lst.pr <- map(tc, prr)
lst.pr$meta.prr %>% dplyr::group_by(kmeans_group) %>% dplyr::summarise(mean = mean(sensitivity))
lst.pr

```
