
```{r}
obj <- st@object
data(gene.anno, package = "scAnno")
data(hcl.sc, package = "scAnno")
data(tcga.data.u, package = "scAnno")
ref.expr <- as.data.frame(Seurat::GetAssayData(hcl.sc, slot = 'data'))
ref.anno <- as.character(Seurat::Idents(hcl.sc))

require(Seurat)
devtools::load_all("~/scAnno/")
results <- scAnno(query = obj,
	ref.expr = ref.expr, ref.anno = ref.anno,
  gene.anno = gene.anno, tcga.data.u = tcga.data.u, use = "Spatial")


```


```{r}
#| copyKAT

st_sub <- getsub(st, cells = grep("Macroph|Epithe", object(st)@meta.data$scsa_cell))
p.map_st_sub <- vis(st_sub)

ka <- job_kat(st_sub, use = "Spatial")
ka <- step1(ka)
ka <- step2(ka)
ka@tables$step2$res_copykat

st_sub <- map(st_sub, ka)
vis(st_sub, "copykat_cell")
vis(st_sub)

```

### inferCNV 判断肿瘤细胞

```{r}
#| inferCNV
# <https://bioconductor.org/packages/release/bioc/html/infercnv.html>
# <https://bioconductor.org/packages/release/bioc/vignettes/infercnv/inst/doc/inferCNV.html>
cn <- asjob_infercnv(st_sub, ref.pattern = "macroph")
cn <- step1(cn)
```

### 细胞注释依据 Nature: A molecular cell atlas of the human lung from single-cell RNA sequencing

A molecular cell atlas of the human lung from single-cell RNA sequencing (PMID: 33208946) [@AMolecularCelTravag2020]

- Supplementary Table 1. Canonical cell types (45) in the human lung and their
  abundances, markers, and available expression data. 
- Supplementary Table 2. Human lung cell cluster identities, abundances, and locations. 
- **Supplementary Table 4**. Enriched markers found in each cluster, with
  transcription factors, receptors/ligands, and disease associated genes
  annotated. 

```{r}
dir.create("AMolecularCelTravag2020", F)
file.copy("~/Downloads/41586_2020_2922_MOESM3_ESM.xlsx", "AMolecularCelTravag2020/nature_sTab_1.xlsx")
file.copy("~/Downloads/41586_2020_2922_MOESM4_ESM.xlsx", "AMolecularCelTravag2020/nature_sTab_2.xlsx")
file.copy("~/Downloads/41586_2020_2922_MOESM6_ESM.xlsx", "AMolecularCelTravag2020/nature_sTab_4.xlsx")
```

```{r}
#| Nature-marker-arrange
nature_xlsx4 <- "AMolecularCelTravag2020/nature_sTab_4.xlsx"
sheet <- 0L
data.nature_xlsx4 <- pbapply::pblapply(openxlsx::getSheetNames(nature_xlsx4),
  function(name) {
    sheet <<- sheet + 1L
    if (!grepl("SS", name)) {
      meta <- openxlsx::read.xlsx(nature_xlsx4, sheet, rows = 1, colNames = F)
      meta <- unlist(meta, use.names = F)
      data <- fxlsx(nature_xlsx4, sheet, startRow = 2)
      namel(meta, data)
    }
  })
data.nature_xlsx4 <- lst_clear0(data.nature_xlsx4)

anno.nature_xlsx4 <- nl(vapply(data.nature_xlsx4, function(x) x$meta, character(1)),
  lapply(data.nature_xlsx4, function(x) x$data))
anno.nature_xlsx4 <- dplyr::rename(data.table::rbindlist(anno.nature_xlsx4, idcol = T),
  cluster = .id, gene = Gene)
anno.nature_xlsx4 <- as_tibble(anno.nature_xlsx4)
```

```{r}
#| Nature-as-marker-list
ref_marker <- as_marker_list(anno.nature_xlsx4, rownames(object(st)))
tt <- map(st, ref_marker, prop = .05, log2fc = .1)
```

### 癌细胞注释依据 Cell: Therapy-Induced Evolution of Human Lung Cancer Revealed by Single-Cell RNA Sequencing

Therapy-Induced Evolution of Human Lung Cancer Revealed by Single-Cell RNA Sequencing [@TherapyInducedMaynar2020]

- **Table S2**. Gene Lists, Related to Figures 1, 2, and 3. Excel file containing
  four sheets of gene lists including 1) Cell type markers 2) COSMIC tier 1
  genes 3) Genes included in each cancer cell signature and 4) Immune markers.

```{r}
#| cancer-cell-markers
dir.create("TherapyInducedMaynar2020", F)
file.copy("~/Downloads/mmc2.xlsx", "TherapyInducedMaynar2020")

fun_cancerSig <- function() {
  file <- "./TherapyInducedMaynar2020/mmc2.xlsx"
  sheets <- openxlsx::getSheetNames(file)
  isthat <- grep("Cancer", sheets)
  fxlsx(file, sheet = isthat)
}
```



```{r}
fig5 <- cls(
  # rw(),
  cl("./Figure+Table/group-1-communication-related-genes-in-pseudotime.pdf"),
  cl("./Figure+Table/group-2-communication-related-genes-in-pseudotime.pdf"),
  cl("./Figure+Table/group-3-communication-related-genes-in-pseudotime.pdf")
)
fig5 <- render(fig5)
fig5
```

```{r eval = T, echo = F, results = "asis"}
#| MAIN-Fig-5
autor(fig5)
```

