

```{r}
geo.ich <- job_geo("GSE167593")
geo.ich <- step1(geo.ich)
geo.ich@params$guess
```

```{r}
x <- ftibble("~/scFEA/input/mouse_example_data.csv")
x <- ftibble("~/scFEA/data/module_gene_iron_m15.csv")

fun_test <- function(file) {
  x <- readLines(file)[-1]
  x <- lapply(strsplit(x, ","), function(x) x[-1])
  unique(unlist(x))
}
x <- fun_test()
```

```{r}
gn.mm <- job_genecard("microglial metabolism")
gn.mm <- step1(gn.mm, restrict = T)
gn.mm@tables$step1
```

```{r}
je <- job_esearch("scRNA-seq metabolism")
vis(je)
```


ftibble("./scfea/balance.csv")
ftibble("./scfea/flux.csv")
readLines("~/scFEA/data/module_gene_complete_mouse_m168.csv")

x <- ftibble("~/scFEA/data/scFEA.M171.mouse.moduleinfo.csv")
a <- ftibble("~/scFEA/data/Human_M168_information.symbols.csv")

fun <- function(x, y) {
  xname <- data.frame(a = x[[1]], b = x[[2]])
  yname <- data.frame(a = y[[1]], b = paste0(y[[3]], "_", y[[5]]))
  dat <- merge(xname, yname, by = "a")
  identical(dat$b.x, dat$b.y)
}
fun(x, y)

mn.mi <- step3(mn.mi, group.by = "seurat_clusters")
mn.mi@plots$step3$gene_module_heatdata$graph_test.sig
sr_sub.mi <- asjob_seurat(mn.mi, 5, rename = )
vis(sr_sub.mi, "regroup.hclust")

```{r}
mn.ast <- do_monocle(sr, "Astrocyte")
mn.ast <- step1(mn.ast, "cellType_group", pre = T)
mn.ast@plots$step1$p.prin
mn.ast <- step2(mn.ast, "Y_2")
mn.ast@plots$step2$p.pseu
mn.ast <- step3(mn.ast, group.by = "seurat_clusters")
mn.ast@plots$step3$gene_module_heatdata$graph_test.sig
```

#### 拟时分析

```{r}
mn.ast <- do_monocle(sr, "Astrocyte")
mn.ast <- step1(mn.ast, "cellType_group", pre = T)
mn.ast@plots$step1$p.prin
mn.ast <- step2(mn.ast, "Y_2")
mn.ast@plots$step2$p.pseu
mn.ast <- step3(mn.ast, group.by = "seurat_clusters")
mn.ast@plots$step3$gene_module_heatdata$graph_test.sig
```
