---
---

```{r include = F, eval = F}
deparse_mail()
info <- items(belong = odate(12), coef = NA)

order_publish()
idname <- order_packaging()
```

```{r include = F}
#| setup
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
autor_preset()
## the package are available at <https://github.com/shaman-yellow/utils.tool>
## if you want to run codes of this Rmarkdown,
## please install the package `utils.tool` and other related packages (run
## install.R)
options(savedir = list(figs = "Figure+Table", tabs = "Figure+Table"))
```

```{r eval = T, echo = F, results = "asis"}
set_cover(info$title)
```

```{r eval = T, echo = F, results = "asis"}
set_index()
```

# 摘要 {#abstract}

Model vs Control

Route:

DEGs -> eQTL -> SNP -> GWAS -> Metabolites and Microbiota

## genes (GWAS) and Metabolites

Mendelian randomization analyses support causal relationships between blood
metabolites and the gut microbiome
[@MendelianRandoLiuX2022]

## Gallstones genes metabolites

## GWAS (SNP) and metabolites

An atlas of genetic influences on human blood metabolites
<https://pubmed.ncbi.nlm.nih.gov/24816252/>

## Gallstones 16s (and metabolites)

<https://pubmed.ncbi.nlm.nih.gov/?term=gallstones%2016s&filter=datesearch.y_10>

Metagenomics of pigmented and cholesterol gallstones: the putative role of bacteria
<https://trace.ncbi.nlm.nih.gov/Traces/?view=study&acc=SRP136827>

Changes and Correlations of the Intestinal Flora and Liver Metabolite Profiles in Mice With Gallstones
<https://www.ncbi.nlm.nih.gov/bioproject/PRJNA736820/>
tables
<https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8416897/>

Carrying asymptomatic gallstones is not associated with changes in intestinal
microbiota composition and diversity but cholecystectomy with significant
dysbiosis
<https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7988160/>

[@InteractionsBeKeren2015]
Interactions between the intestinal microbiota and bile acids in gallstones patients

Biliary Microbiota and Bile Acid Composition in Cholelithiasis
<https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7352139/>
16s RNA seq
<https://www.ebi.ac.uk/ena/browser/view/PRJEB12755>

Patients with Primary and Secondary Bile Duct Stones Harbor Distinct Biliary
Microbial Composition and Metabolic Potential
<https://www.ncbi.nlm.nih.gov/pmc/articles/PMC9082501/>
16s 
<https://www.ncbi.nlm.nih.gov/bioproject/PRJNA580086/>

Biliary Microbial Structure of Gallstone Patients With a History of Endoscopic Sphincterotomy Surgery
16s
bile microbiome
<https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7873689/>

```{r}
dic(di("胆结石"),
  di("胆固醇"),
  di("蛋白质组学"),
  di(en = "Cholesterol Gallstone Disease")
)

# G: gallstones 胆结石
# C: cholesterol 胆固醇
# P: proteomics 蛋白质组学
# CGD: Cholesterol Gallstone Disease 胆固醇胆结石疾病
```

# 前言 {#introduction}

# 材料和方法 {#methods}

## 材料

```{r eval = T, echo = F, results = "asis"}
auto_material()
```

## 方法

```{r eval = T, echo = F, results = "asis"}
auto_method()
```

# 分析结果 {#results}

# 结论 {#dis}

# 附：分析流程 {#workflow}
