
#### GSE227641: HCT 15 cells with oxaliplatin and sorafenib; CoCl2, brefeldin A, or low glucose

-	Inositol hexaphosphate enhances chemotherapy by reversing persistent endoplasmic reticulum stress-induced senescence in colorectal cancer
    - for HCT 15 cells treated with oxaliplatin and sorafenib.
        - GSE227609
    - for HCT 15 cells treated with CoCl2, brefeldin A, or low glucose.
        - GSE227379

```{r}
geo3 <- job_geo("GSE227641")
geo3 <- step1(geo3)
geo3@params$guess
geo3 <- step2(geo3)

untar("./GSE227641/GSE227641_RAW.tar", exdir = "./GSE227641")
lapply(list.files("./GSE227641", "gz$", full.names = T), R.utils::gunzip)

metadata <- geo3@params$guess
counts <- lapply(list.files("./GSE227641", "txt$", full.names = T), ftibble)
```

#### GSE183984: tumor tissue obtained before and after cetuximab treatment

- RNA sequencing of formalin-fixed paraffin-embedded (FFPE) tumor tissue obtained before and after cetuximab treatment
    - GSE183984

```{r}
geo4 <- job_geo("GSE183984")
geo4 <- step1(geo4)
geo4 <- step2(geo4, "counts")

metadata <- geo4@params$guess
metadata <- filter(metadata, grepl("primary tumor", tissue.ch1))
```


