
#### GSE156281: post chemo-RT surgical materials of RCA patients

- Total of 104 patients RNA samples (pre-therapeutic biopsies) belonging to patients of pathological complete and non complete response post radiotherapy. Addiotional 12 RNA samples from post chemo-RT surgical materials of RCA patients.
    - GSE156281



#### GSE227641: HCT 15 cells with oxaliplatin and sorafenib; CoCl2, brefeldin A, or low glucose

-	Inositol hexaphosphate enhances chemotherapy by reversing persistent endoplasmic reticulum stress-induced senescence in colorectal cancer
    - for HCT 15 cells treated with oxaliplatin and sorafenib.
        - GSE227609
    - for HCT 15 cells treated with CoCl2, brefeldin A, or low glucose.
        - GSE227379

```{r}
geo3 <- job_geo("GSE227641")
geo3 <- step1(geo3)
geo3@params$guess
geo3 <- step2(geo3)

untar("./GSE227641/GSE227641_RAW.tar", exdir = "./GSE227641")
lapply(list.files("./GSE227641", "gz$", full.names = T), R.utils::gunzip)

metadata <- geo3@params$guess
counts <- lapply(list.files("./GSE227641", "txt$", full.names = T), ftibble)
```

#### GSE183984: tumor tissue obtained before and after cetuximab treatment

- RNA sequencing of formalin-fixed paraffin-embedded (FFPE) tumor tissue obtained before and after cetuximab treatment
    - GSE183984

```{r}
geo4 <- job_geo("GSE183984")
geo4 <- step1(geo4)
geo4 <- step2(geo4, "counts")

metadata <- geo4@params$guess
metadata <- filter(metadata, grepl("primary tumor", tissue.ch1))
```

### GSE111017: Study of sarcopenia in human muscle biopsies of elderly individuals

```{r}
geo6 <- job_geo("GSE111017")
geo6 <- step1(geo6)
geo6@params$prods@.Data %<>% lapply(function(x) x[1])
geo6@params$prods
geo6@params$guess
```

#### "GSE111006", "GSE111010", "GSE111016"

```{r}
counts.lst <- pbapply::pblapply(c("GSE111006", "GSE111010", "GSE111016"),
  function(gse) {
    if (!file.exists(gse)) {
      geo <- job_geo(gse)
      geo <- step1(geo)
      geo <- step2(geo, "Counts")
    }
    file <- list.files(gse, ".gz$", full.names = T)
    if (length(file) > 0)
      R.utils::gunzip(file)
    file <- list.files(gse, ".csv$", full.names = T)
    ftibble(file)
  })

counts.lst 
```


```{r}
#| lasso
la5 <- asjob_lasso(lm5, use.filter = lm5@tables$step2$tops[[1]]$hgnc_symbol, use = "hgnc_symbol")
la5 <- step1(la5, levels = c("OLD_Healthy", "OLD_Sarcopenia"), n.train = .7)
la5@plots$step1$p.consist
la5 <- step2(la5)
la5@plots$step2$p.efs
la5 <- step3(la5, nfold = 3, use_tops = T)

la5@plots$step3$p.roc$lambda.min
la5@params$tops

```

```{r}

lm5@tables$step2$tops[[1]]$hgnc_symbol
intersect(lm5@tables$step2$tops[[1]]$hgnc_symbol, all.sigs)

```
