---
---

```{r include = F, eval = F}
deparse_mail()
info <- items(belong = odate(4), eval = ic())
show.ic(info)

order_publish()
idname <- order_packaging()
```

```{r include = F}
#| setup
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
autor_preset()
## the package are available at <https://github.com/shaman-yellow/utils.tool>
## if you want to run codes of this Rmarkdown,
## please install the package `utils.tool` and other related packages (run
## install.R)
options(savedir = list(figs = "Figure+Table", tabs = "Figure+Table"))
```

```{r eval = T, echo = F, results = "asis"}
set_cover(info$title)
```

```{r eval = T, echo = F, results = "asis"}
set_index()
```

# 摘要 {#abstract}

1、能否发表关于ADHD（儿童注意力缺陷多动障碍）的生信文章
2、或者是ADHD与过敏类疾病（如过敏性鼻炎）的生信文章
3、如果可以发表，有没有建议的拟题

Attention deficit/hyperactivity disorder (ADHD)

microbiota-gut-brain axis

题目暂定：通过预测因果基因 (CG, causal genes) 及结合表达量分析关联微生物-肠-脑轴探究 ADHD 疾病机制

ADHD 在下述各个领域都有不同程度的研究发现，但目前缺乏集成各个环节的更完整的研究，故拟题。

- 因果基因分析，结合 GWAS 和 eQTL 数据发现因果基因
- RNA-seq 基因表达分析
- 代谢物分析
- 肠道菌分析
- 代谢物-微生物-肠-脑轴分析
- ...
- 上述思路获得结果后的集成分析。


```{r}
dic(di("差异表达基因", "Differential Expressed Genes", "DEGs"))

```

# 前言 {#introduction}

# 材料和方法 {#methods}

## 材料

```{r eval = T, echo = F, results = "asis"}
auto_material()
```

## 方法

```{r eval = T, echo = F, results = "asis"}
auto_method()
```

# 分析结果 {#results}

# 结论 {#dis}

# 附：分析流程 {#workflow}

Sherlock: detecting gene-disease associations by matching patterns of expression QTL and GWAS
SMR: Integration of summary data from GWAS and eQTL studies predicts complex trait gene targets

## ADHD 

### eQTL

大脑

### GWAS

Review: PMID: 33495110
<https://www.sciencedirect.com/science/article/pii/S0924977X21000067?via%3Dihub>

### Mendelian randomization (MR)

PMID: 36124769
Association Between Human **Blood Metabolome** and the Risk of Psychiatric Disorders
<https://pubmed.ncbi.nlm.nih.gov/36124769/>

PMID: 37168108
Two-sample Mendelian randomization analysis investigates causal associations
between **gut microbiota** and attention deficit hyperactivity disorder
<https://pubmed.ncbi.nlm.nih.gov/37168108/>

### Microbiota

(main data)
Gut microbiome in ADHD and its relation to neural reward anticipation
<https://pubmed.ncbi.nlm.nih.gov/28863139/>

PMID: 26046241
Gut-Microbiota-Brain Axis and Its Effect on Neuropsychiatric Disorders With Suspected Immune Dysregulation
<https://pubmed.ncbi.nlm.nih.gov/26046241/>
(influence the immune and nervous systems)

PMID: 37233633
Understanding the ADHD-Gut Axis by Metabolic Network Analysis.
<https://pubmed.ncbi.nlm.nih.gov/37233633/>

### transcriptome

Integrated Analysis of microRNA and mRNA Expression Profiles: An Attempt to Disentangle the Complex Interaction Network in Attention Deficit Hyperactivity Disorder
<https://www.mdpi.com/2076-3425/9/10/288>

(no data)
Immune signatures and disorder-specific patterns in a cross-disorder gene expression analysis
<https://www.cambridge.org/core/journals/the-british-journal-of-psychiatry/article/immune-signatures-and-disorderspecific-patterns-in-a-crossdisorder-gene-expression-analysis/A35E995DD31A2174FE998C5F09FBA6CF>

GSE205129 (WBC?)

### Epigenetic modification


