


x <- PubChemR::get_properties(
  properties = "LiteratureCount",
  identifier = "aspirin",
)


.add_properties.PubChemR()
maps <- PubChemR:::property_map 
maps


```{r}
x <- get_ctd_data()
y <- dplyr::filter(x$CTD_diseases, grpl(DiseaseName, "colitis", T))
y <- dplyr::filter(x$CTD_chemicals_diseases, DiseaseID %in% y$DiseaseID)

```



je.bio <- job_esearch("drug Bioactivity")
vis(je.bio)



```{r}
vn$runs
lapply(vn$runs, function(x) vn$res.ligand[[ x[1] ]])
lapply(vn$runs, function(x) vn$res.receptor[[ x[2] ]])
```

en.top@step <- 1L
en.top <- step2(en.top, "hsa05321")
en.top@plots$step2$p.pathviews$hsa05321$ins
en.top@tables$step2$res.pathviews


```{r eval = T, echo = F, results = "asis"}
#| TOP-hsa05321-visualization
autor(en.top@plots$step2$p.pathviews$hsa05321)
```


```{r}
pretty_docking("9ilb.pdbqt", "72326_into_9ilb_out.pdbqt", "vina_space/72326_into_9ilb")
```


```{r}
txt <- pdftools::pdf_text("./material/note.pdf")
```


tc2@params$dbs %<>% lapply(
  function(x) {
    x@db <- data.frame()
    x
  })


link <- tc2@params$link
ele <- link$findElement("xpath", paste0("//div[@class='el-radio-group']//span[text()='", "Ingredients", "']/.."))
ele$clickElement()


x <- tc2@params$link$getPageSource()
get_table.html(x[[1]])

link <- start_drive(port = 8888)
link$open()

"//div//input[@class='el-input__inner']"

ele <- link$findElement("xpath", paste0("//span[@class='el-pagination__sizes']",
    "//i[@class='el-icon el-select__caret el-select__icon']"))

ele$clickElement()

link <- tc2@params$link
ele2 <- link$findElement("xpath", "//ul[@role='listbox']//li//span[contains(text(), '200条/页')]")
ele2 <- link$findElement("xpath", "//ul[@role='listbox']//li//span[text()='200条/页']")
ele2$clickElement()

x <- tc2@params$link$getPageSource()
y <- get_table.html(x[[1]])

# 黄柏
strx(x[[1]], ".{200}100条.{200}")


tc <- job_tcga("")
tc <- step1(tc)

tc <- job_tcmsp(herbs)
tc <- step1(tc)


bt <- job_batman(herbs)
bt <- slice(bt, 1:10)
bt <- step1(bt)
bt <- step2(bt)
bt <- step3(bt)

bt@plots$step3$p.pharm
bt@params$compounds_info


#### 与肠道炎症相关的通路和基因

```{r eval = T, echo = F, results = "asis"}
#| HERBS-hsa05321-visualization
autor(en.herbs@plots$step2$p.pathviews$hsa05321)
```

```{r}

#### 与肠道炎症相关的通路和基因

```{r eval = T, echo = F, results = "asis"}
#| HERBS-hsa05321-visualization
autor(en.herbs@plots$step2$p.pathviews$hsa05321)
```


```{r eval = T, echo = F, results = "asis"}
#| Metadata-of-visualized-Docking
autor(vn@tables$step6$data)
```

```{r eval = T, echo = F, results = "asis"}
#| Docking-72326-into-9ilb
autor(vn@plots$step6$Top1_72326_into_9ilb)
```

```{r eval = T, echo = F, results = "asis"}
#| Docking-969516-into-4xfu
autor(vn@plots$step6$Top2_969516_into_7kxw)
```

```{r eval = T, echo = F, results = "asis"}
#| Docking-774-into-nod2
autor(vn@plots$step6$Top3_644019_into_8dc8)
```


```{r eval = T, echo = F, results = "asis"}
#| Docking-72326-into-9ilb-detail
autor(vn@plots$step7$Top1_72326_into_9ilb)
```

```{r eval = T, echo = F, results = "asis"}
#| Docking-969516-into-4xfu-detail
autor(vn@plots$step7$Top2_969516_into_7kxw)
```

```{r eval = T, echo = F, results = "asis"}
#| Docking-774-into-nod2-detail
autor(vn@plots$step7$Top3_644019_into_8dc8)
```


### Top1 的靶点的富集分析

```{r eval = T, echo = F, results = "asis"}
#| TOP-KEGG-enrichment
autor(en.top@plots$step1$p.kegg$ids)
```

```{r eval = T, echo = F, results = "asis"}
#| TOP-GO-enrichment
autor(en.top@plots$step1$p.go$ids)
```

```{r eval = T, echo = F, results = "asis"}
#| TOP-pharmacology-visualization
autor(p.alluTop.dis)
```

```{r}
cpd.top <- dplyr::filter(cpds.int.ctd, cids %in% vn@tables$step6$data$PubChem_id[1])
en.top <- job_enrich(cpd.top$Target.name)
en.top <- step1(en.top)
en.top@plots$step1$p.kegg
en.top@tables$step1$res.kegg$ids
p.alluTop.dis <- new_allu(cpd.top, axes = 1:3, trunc = T)

p.alluTop.all <- new_allu(
  dplyr::filter(tc2@params$data.allu, Ingredient.name %in% unique(cpd.top$Ingredient.name)), axes = 1:3, trunc = T)
p.alluTop.all
```

#### TOP1 的结合靶点 (IL1B) 参与的通路

```{r eval = T, echo = F, results = "asis"}
#| IL1B-kegg
autor(path.il1b)
```

```{r eval = T, echo = F, results = "asis"}
#| IL1B-go
autor(pathGo.il1b)
```

```{r}
pathKegg.il1b <- filter(en.top, "IL1B")
path.il1b

pathGo.il1b <- filter(en.top, "IL1B", use = "go")
pathGo.il1b
```


```{r}
vn <- step6(vn, top = 3, unique = T)
vn@plots$step6$Top1_72326_into_9ilb
vn@plots$step6$Top2_969516_into_7kxw
vn@plots$step6$Top3_644019_into_8dc8
vn@tables$step6$data
vn <- step7(vn)
vn@plots$step7$Top1_72326_into_9ilb
vn@plots$step7$Top2_969516_into_7kxw
vn@plots$step7$Top3_644019_into_8dc8
```


```{r}
# https://www.tcmsp-e.com/#/
tc2 <- job_tcmsp2(herbs)
tc2 <- step1(tc2)
tc2 <- step2(tc2)
tc2 <- step3(tc2, cl = 10)
tc2@tables$step2$ingredients
tc2@tables$step2$compounds_targets
tc2@plots$step3$p.pharm


```

```{r eval = T, echo = F, results = "asis"}
#| 3081405-targets
autor(dplyr::filter(tc2@params$easyRead, Ingredient.id == 3081405))
```


```{r}
vn2 <- job_vina(c(kaempferol = 5280863), "ALOX5")
vn2 <- step1(vn2)
vn2 <- step2(vn2)
vn2 <- step3(vn2)
vn2 <- step4(vn2)
vn2 <- step5(vn2)
```
