---
---

```{r include = F}
deparse_mail()
```

```{r include = F}
#| setup
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
autor_preset()
## the package are available at <https://github.com/shaman-yellow/utils.tool>
## if you want to run codes of this Rmarkdown,
## please install the package `utils.tool` and other related packages (run
## install.R)
options(savedir = list(figs = "Figure+Table", tabs = "Figure+Table"))
```

```{r eval = T, echo = F, results = "asis"}
set_cover("title")
```

```{r eval = T, echo = F, results = "asis"}
set_index()
```

# 摘要 {#abstract}

质子磁共振光谱法 (H-MRS) 
加巴喷丁 (Gabapentin)
重复经颅磁刺激治疗 (repeat transcranial magnetic stimulation, rTMS)
不完全性脊髓损伤 (Incomplete spinal cord injury, iSCI) 
神经病理性疼痛 (neuropathic pain, NP) 

iSCI
- GSE226238
- GSE133093
NP
- GSE115565
rTMS
- Transcriptional changes in the (rat) brain induced by repetitive transcranial magnetic stimulation
- GSE206765 (16s)

GEO 有 iSCI、NP、rTMS 各自的基因表达数据集，可以从三者之间的关联性寻找 rTMS 可能的疗效和机制

# 前言 {#introduction}

# 材料和方法 {#methods}

## 材料

```{r eval = T, echo = F, results = "asis"}
auto_material()
```

## 方法

```{r eval = T, echo = F, results = "asis"}
auto_method()
```

# 分析结果 {#results}

# 结论 {#dis}

# 附：分析流程 {#workflow}
