

```{r}
set.seed(2020)
s <- Cardinal::simulateSpectra(n = 9, npeaks = 10, from = 500, to = 600)

coord <- expand.grid(x = 1:3, y = 1:3)
run <- factor(rep("run0", nrow(coord)))

fdata <- Cardinal::MassDataFrame(mz = s$mz)
pdata <- Cardinal::PositionDataFrame(run = run, coord = coord)
pdata

out <- Cardinal::MSImagingExperiment(
  spectraData = s$intensity,
  featureData = fdata,
  pixelData = pdata
)
out

Cardinal::image(out, mz = 550)
```

```{r}
stn <- job_seuratn(c(
    "/media/echo/6E3CE3153CE2D75D/曹卓测序结果/空间转录组/肺癌空间转录组测序/CellRanger/Cancer_1/outs/raw_feature_bc_matrix/",
    "/media/echo/6E3CE3153CE2D75D/曹卓测序结果/空间转录组/肺癌空间转录组测序/CellRanger/Para_cancer_1/outs/raw_feature_bc_matrix/"), mode = "sc")
stn <- step1(stn, NULL)
```


```{r}
st.cancer1 <- job_seuratSp("/media/echo/6E3CE3153CE2D75D/曹卓测序结果/空间转录组/肺癌空间转录组测序/CellRanger/Cancer_1/outs/")
st.cancer1 <- step1(st.cancer1)
st.cancer1 <- step2(st.cancer1, 2500, 9000)
st.cancer1 <- step3(st.cancer1, 1:15, 2)
st.cancer1 <- step4(st.cancer1)

wrap(st.cancer1@plots$step4$p.map_SingleR, 7, 5)

st.cancer1 <- step5(st.cancer1, 5)
st.cancer1 <- step6(st.cancer1, "Lung")

```


fe@tables$step1$t.hypergeom$ids %>% 
  dplyr::rename(Description = KEGG.name, Count = CompoundHits, pvalue = p.value) %>% 
  plot_kegg(use = "pvalue", ratio = "Compound_Ratio")


get_data.mtest <- function(x, i) {
  x <- lapply(x[ i ],
    function(obj) {
      obj$data
    })
  names(x) <- paste0("I = ", i)
  frbind(x, idcol = "features")
}
x <- get_data.mtest(car.integrate$mtest, 1:10)
.map_boxplot2(x, T, x = "group", y = "intensity", ids = "features", scales = "free_y",
  xlab = "Group", ylab = "Normalized Itensity")


### Limma 差异分析

```{r}
counts <- dplyr::select(quant, id, tidyselect::contains("area"))
counts <- dplyr::rename_with(counts,
    function(x) gs(x, ".*Peak.Area[.]*(\\w+\\.\\w).*", "\\1"),
    tidyselect::contains("area")
)
counts <- dplyr::mutate(counts, dplyr::across(dplyr::where(is.double), function(x) log2(x + 1)))
counts
genes <- dplyr::select(quant, -tidyselect::contains("area"))
genes <- dplyr::relocate(genes, id)
genes
metadata <- group_strings(colnames(counts)[-1], c("Control" = "Adj", "Cancer" = "Tumor"), "sample")
metadata

lm.meta <- job_limma_normed(counts, metadata, genes)
lm.meta <- step1(lm.meta)
lm.meta <- step2(lm.meta, Cancer - Control, label = "Name")
lm.meta@plots$step2$p.volcano$`Cancer - Control`
Tops <- lm.meta@tables$step2$tops$`Cancer - Control`
Tops <- map(Tops, "rownames", genes, "id", "KEGG", col = "KEGG")
Tops

```

```{r eval = T, echo = F, results = "asis"}
#| META-data-Cancer-vs-Control-DEGs
autor(Tops)
```

### FELLA 代谢物富集分析

```{r}
fe <- job_fella(rm.no(Tops$KEGG))
fe <- step1(fe)
fe@params$enrich.lst$ids@hypergeom
fe@plots$step1$p.enrich
fe@tables$step1$t.enrich
fe@params$resTable$ids

fe@plots$step1$p.hypergeom$ids
```

```{r eval = T, echo = F, results = "asis"}
#| Compounds-hypergeom-KEGG-enrichment
autor(fe@plots$step1$p.hypergeom$ids)
```


fella.tops
lm.flux
p.venn <- new_venn(diff_meta = fella.tops$inputs$ids, diff_flux = unlist(Tops.flux$kegg))
p.venn$ins

intersect

p.hpFlux <- map.fluxGene(mn.integrated, inter.lst$data, branches = list(c("Y_13", "Y_4")),
  enrich = en.flux, HLs = list(Top_1000_graph_test = genes.Top_1000_graph_test))
wrap(p.hpFlux, 10, 8)

genes.Tops2meta <- intersect(unique(p.hpFlux@data@data$rownames), genes.Top_1000_graph_test)
genes.Tops2meta

p.dimsGene <- focus(mn.integrated@params$sr_sub, genes.Tops2meta, "Integrated_cells")
p.dimsGene$p.vln
p.dimsGene$p.dim

p.testTop5 <- focus(mn.integrated@params$sr_sub, head(mn.integrated@tables$step3$graph_test.sig$gene_id, 10), "Integrated_cells")
p.testTop5$p.dim


p.hpFlux <- map.fluxGene(mn.integrated, inter.lst$data, branches = list(c("Y_13", "Y_4")),
  enrich = en.flux, HLs = list(Top_1000_graph_test = genes.Top_1000_graph_test))
wrap(p.hpFlux, 10, 8)

genes.Tops2meta <- intersect(unique(p.hpFlux@data@data$rownames), genes.Top_1000_graph_test)
genes.Tops2meta

p.dimsGene <- focus(mn.integrated@params$sr_sub, genes.Tops2meta, "Integrated_cells")
p.dimsGene$p.vln
p.dimsGene$p.dim

p.testTop5 <- focus(mn.integrated@params$sr_sub, head(mn.integrated@tables$step3$graph_test.sig$gene_id, 10), "Integrated_cells")
p.testTop5$p.dim


### 空间代谢

#### files

```{r}
.file_fig("/media/echo/6E3CE3153CE2D75D/曹卓测序结果/空间代谢组/YAS202310270001-1/YAS202310270001-1/Result/03_Bioinformatic_Analysis/01_ROC_Analysis/Differential_Analysis_Data.xlsx")
.file_fig("/media/echo/6E3CE3153CE2D75D/曹卓测序结果/空间代谢组/YAS202310270001-1/YAS202310270001-1/Result/03_Bioinformatic_Analysis/02_Co-location_Analysis/Co-location_Data.xlsx")
```

```{r}
# Tumor-1, Adjacent-1, Tumor-2, Adjacent-2
.file_fig("/media/echo/6E3CE3153CE2D75D/曹卓测序结果/空间代谢组/原始数据/YAS202310270001-1_raw data/img039.jpg")
.file_fig("/media/echo/6E3CE3153CE2D75D/曹卓测序结果/空间代谢组/原始数据/YAS202310270001-1_raw data/img039_0001.jpg")
```

```{r}
.file_fig("/media/echo/6E3CE3153CE2D75D/曹卓测序结果/空间代谢组/YAS202310270001-1/YAS202310270001-1/Result/01_Optical Image_Result/02_HE_Stain/Tumor-1.tif")
.file_fig("/media/echo/6E3CE3153CE2D75D/曹卓测序结果/空间代谢组/YAS202310270001-1/YAS202310270001-1/Result/01_Optical Image_Result/02_HE_Stain/Adjacent-1.tif")
.file_fig("/media/echo/6E3CE3153CE2D75D/曹卓测序结果/空间代谢组/YAS202310270001-1/YAS202310270001-1/Result/01_Optical Image_Result/02_HE_Stain/Tumor-2.tif")
.file_fig("/media/echo/6E3CE3153CE2D75D/曹卓测序结果/空间代谢组/YAS202310270001-1/YAS202310270001-1/Result/01_Optical Image_Result/02_HE_Stain/Adjacent-2.tif")
readLines("/media/echo/6E3CE3153CE2D75D/曹卓测序结果/空间代谢组/原始数据/YAS202310270001-1_raw data/")
```



```{r}
test <- openai::create_chat_completion(
  model = "gpt-3.5-turbo",
  messages = list(
    list(
      "role" = "system",
      "content" = "You are a helpful assistant."
      )),
  openai_api_key = getOption("OPENAI_API_KEY")
)
```


