

test

```{r}
tc <- job_tcga("TCGA-BRCA")
tc <- step1(tc)
tc <- filter(tc, use.tnbc = T)
tc <- step2(tc)
tc.rna <- step3(tc, clinical.info = "drug")

lm.rna <- asjob_limma(tc.rna)
lm.rna@params$.metadata

usedDrug <- frbind(lm.rna@params$.metadata$treatments, fill = T)
usedDrug

```


```{r}
je <- job_esearch("Multidrug Resistance")
vis(je, col = c("SortPubDate", "Title"))
je@object$Title %>% grpf("Multi.?drug", T)
je@object$Title[27]

je@object[70, ]

og <- job_ogwas("Multidrug Resistance")
og@object

```

多药耐药(multidrug resistance，MDR)是指肿瘤细胞对一种化疗药物产生耐药的同时，对其他结构和作用机制不同的化疗药物也产生交叉耐药的现象，是导致化疗失败的主要原因


```{r}


ep <- job_epifactor()
ep <- step1(ep)
ep@tables$step1$protein

p.venn <- new_venn(TNBC_MDR = p.venn_mdr2tnbc$ins, EpiFactors = ep@tables$step1$protein$HGNC_symbol)
p.venn

en.epi <- job_enrich(p.venn$ins)
en.epi <- step1(en.epi)
en.epi@plots$step1$p.kegg$ids
en.epi <- step2(en.epi, "hsa05206")
en.epi@plots$step2$p.pathviews$hsa05206
```


- Multidrug Resistance [@MechanismsOfMBukows2020]
    - Cisplatin
    - Etoposide
    - Castration *
    - Taxane *
- TNBC (MDR PMID:34357119 [@InvestigationalDamask2021])
    -  The mechanisms of MDR include elevated metabolism of xenobiotics,
      enhanced efflux of drugs, growth factors, increased DNA repair capacity,
      and genetic factors (gene mutations, amplifications, and epigenetic
      alterations)


### KEGG、GO

```{r}
en.cus <- job_enrich(genes.custom, annotation = en@params$annotation)
en.cus <- step1(en.cus)
en.cus@plots$step1$p.kegg
en.cus@plots$step1$p.go
en.cus@tables$step1$res.kegg
en.cus@tables$step1$res.go
```


dat <- dplyr::filter(lm.br@object$samples, gs(sample, "[A-Z]$", "") %in% pb.rot@object$TCGA_SAMPLE)
dat$isTumor


```{r}
geo.tnbc <- job_geo("GSE264252")
geo.tnbc <- step1(geo.tnbc)
geo.tnbc@params$guess
```

