---
---

```{r include = F}
#| setup
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
autor_preset()
## the package are available at <https://github.com/shaman-yellow/utils.tool>
## if you want to run codes of this Rmarkdown,
## please install the package `utils.tool` and other related packages (run
## install.R)
options(savedir = list(figs = "Figure+Table", tabs = "Figure+Table"))
```

```{r eval = T, echo = F, results = "asis"}
set_index()
```

# 摘要 {#abstract}

糖尿病视网膜病变与眼底图像的计量分析

## DR tools

EyePACS: an adaptable telemedicine system for diabetic retinopathy screening (20144289)

Automated Diabetic Retinopathy Screening and Monitoring Using Retinal Fundus Image Analysis (26888972) [@AutomatedDiabeBhaska2016]

## Others

Chákṣu: A glaucoma specific fundus image database (36737439)

Assessment of image quality on color fundus retinal images using the automatic retinal image analysis (35729197)
Kaggle database



# 前言 {#introduction}

# 研究设计流程图 {#route}

```{r}
#| route
route <- as_network(
  list("RNA_seq_data:Preprocess",
    ), "tree"
)
p.route <- flowChart(route, 1.1, 1)
```

```{r, eval = T, echo = F, fig.width = 10, fig.height = 7, fig.cap = NULL}
p.route
```

# 材料和方法 {#methods}

# 分析结果 {#results}

# 结论 {#dis}

# 附：分析流程 {#workflow}
