---
---

```{r include = F}
deparse_mail()
```

```{r include = F}
#| setup
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
autor_preset()
## the package are available at <https://github.com/shaman-yellow/utils.tool>
## if you want to run codes of this Rmarkdown,
## please install the package `utils.tool` and other related packages (run
## install.R)
options(savedir = list(figs = "Figure+Table", tabs = "Figure+Table"))
```

```{r eval = T, echo = F, results = "asis"}
set_index()
```

# 题目

光学相干断层扫描血管成像技术 (OCTA) 在糖尿病视网膜病变 (DR) 中的应用

# 摘要 {#abstract}

糖尿病视网膜病变 (diabetic retinopathy, DR)
光学相干断层扫描血管成像技术 (Optical Coherence Tomography Angiography, OCTA)

- 时间分布 (发表) (趋势) 
- 国家
- 协作 
- 引用
- Top 10 keywords with the strongest citation
- top 10 article
- top country
- Collaboration
- The co-occurrence map of keywords

topic:

- Trend analysis of publications and citations
- Publication pattern and collaboration analysis
- Research domains and targeted sources
- Keywords analysis

# 前言 {#introduction}

# 材料和方法 {#methods}

## 材料

```{r eval = T, echo = F, results = "asis"}
auto_material()
```

## 方法

```{r eval = T, echo = F, results = "asis"}
auto_method()
```

Web of Science Core Collection (WoSCC)

# 分析结果 {#results}

# 结论 {#dis}

# 附：分析流程 {#workflow}

```{r}
kds <- list(
  dr = c("diabetic retinopathy", "diabetic macular edema",
    "diabetic retinal damage", "diabetic retina"
    ),
  octa = c("Optical Coherence Tomography Angiography",
    "OCT Angiography", "OCTA"
  )
)

bi <- job_biblio(kds)
bi <- step1(bi, 2)
bi@params$summary
bi@tables$step1$alls$YY
bi <- step2(bi)
bi@plots$step2$p.most_ave

```

